---
title: "Association between dependent measures and T-1000 self-reported"
author: "Saeid Parvandeh"
date: "Febrary 6, 2017"
output: html_document
---

Read csv self repoted file:

```{r}
rm(list=ls())
measured_scores <- read.csv("E:/LIBR/Data/Measured_Scores.csv")
self_reports <- read.csv("E:/LIBR/Data/CompleteT1000_2.csv")
narratives <- read.csv("E:/LIBR/Data/T1000_LifechartNarratives_Scores.csv")
common_ids <- intersect(as.vector(narratives[, 1]), as.vector(self_reports[, 1]))
self_reports <- self_reports[which(self_reports[, 1]%in%common_ids), ]
self_reports <- self_reports[order(self_reports$id), ]
narratives <- narratives[which(narratives[, 1]%in%common_ids), ]
measured_scores <- measured_scores[which(measured_scores[, 1]%in%common_ids), ]
```

Extract Mood/Anxiety and Healthy Control groups:

```{r}
SelfReport_M.A <- subset(self_reports, GroupAssignment=="Mood/Anxiety")
dim(SelfReport_M.A)
Narratives_M.A <- narratives[which(self_reports$GroupAssignment=="Mood/Anxiety"), ]
MeasrdScore_M.A <- measured_scores[which(self_reports$GroupAssignment=="Mood/Anxiety"), ]
SelfReport_H <- subset(self_reports, GroupAssignment=="Healthy Control")
dim(SelfReport_H)
Narratives_H <- narratives[which(self_reports$GroupAssignment=="Healthy Control"), ]
MeasrdScore_H <- measured_scores[which(self_reports$GroupAssignment=="Healthy Control"), ]
```

Comparing the number of total words in mood/anxiety and healthy/control groups

```{r}
hist(MeasrdScore_M.A$X..total.words, col = "blue", main = "Histogram of total number of words",
     xlab = "Number of words")
hist(MeasrdScore_H$X..total.words, col = "purple", add = TRUE)
legend("topright", c("Mood and Anxiety", "Healthy Control"), col =c("blue","purple"), lwd = 10)
```

Association of total number of words and adjective words with PHQ, OASIS, AND CTQ

```{r}
# mood and anxiety
total_words_M.A <- MeasrdScore_M.A$X..total.words
adj_words_M.A <- MeasrdScore_M.A$X..of.sub_words
PHQ_M.A <- SelfReport_M.A$PHQ
OASIS_M.A <- SelfReport_M.A$OASIS
CTQ_M.A <- SelfReport_M.A$CTQ_score
par(mfrow = c(2, 3))
lm.fit_PHQ <- lm(total_words_M.A ~ PHQ_M.A)
plot(PHQ_M.A, total_words_M.A, main = "effect of PHQ", xlab = "PHQ", ylab = "Total words")
abline(lm.fit_PHQ)
lm.fit_OASIS <- lm(total_words_M.A ~ OASIS_M.A)
plot(OASIS_M.A, total_words_M.A, main = "effect of OASIS", xlab = "OASIS", ylab = "Total words")
abline(lm.fit_OASIS)
lm.fit_CTQ <- lm(total_words_M.A ~ CTQ_M.A)
plot(CTQ_M.A, total_words_M.A, main = "effect of CTQ", xlab = "CTQ", ylab = "Total words")
abline(lm.fit_CTQ)
lm.fit_PHQ <- lm(adj_words_M.A ~ PHQ_M.A)
plot(PHQ_M.A, adj_words_M.A, main = "effect of PHQ", xlab = "PHQ", ylab = "Adjective words")
abline(lm.fit_PHQ)
lm.fit_OASIS <- lm(adj_words_M.A ~ OASIS_M.A)
plot(OASIS_M.A, adj_words_M.A, main = "effect of OASIS", xlab = "OASIS", ylab = "Adjective words")
abline(lm.fit_OASIS)
lm.fit_CTQ <- lm(adj_words_M.A ~ CTQ_M.A)
plot(CTQ_M.A, adj_words_M.A, main = "effect of CTQ", xlab = "CTQ", ylab = "Adjective words")
abline(lm.fit_CTQ)
# healthy control
total_words_H <- MeasrdScore_H$X..total.words
adj_words_H <- MeasrdScore_H$X..of.sub_words
PHQ_H <- SelfReport_H$PHQ
OASIS_H <- SelfReport_H$OASIS
CTQ_H <- SelfReport_H$CTQ_score
par(mfrow = c(2, 3))
lm.fit_PHQ <- lm(total_words_H ~ PHQ_H)
plot(PHQ_H, total_words_H, main = "effect of PHQ", xlab = "PHQ", ylab = "Total words")
abline(lm.fit_PHQ)
lm.fit_OASIS <- lm(total_words_H ~ OASIS_H)
plot(OASIS_H, total_words_H, main = "effect of OASIS", xlab = "OASIS", ylab = "Total words")
abline(lm.fit_OASIS)
lm.fit_CTQ <- lm(total_words_H ~ CTQ_H)
plot(CTQ_H, total_words_H, main = "effect of CTQ", xlab = "CTQ", ylab = "Total words")
abline(lm.fit_CTQ)
lm.fit_PHQ <- lm(adj_words_H ~ PHQ_H)
plot(PHQ_H, adj_words_H, main = "effect of PHQ", xlab = "PHQ", ylab = "Adjective words")
abline(lm.fit_PHQ)
lm.fit_OASIS <- lm(adj_words_H ~ OASIS_H)
plot(OASIS_H, adj_words_H, main = "effect of OASIS", xlab = "OASIS", ylab = "Adjective words")
abline(lm.fit_OASIS)
lm.fit_CTQ <- lm(adj_words_H ~ CTQ_H)
plot(CTQ_H, adj_words_H, main = "effect of CTQ", xlab = "CTQ", ylab = "Adjective words")
abline(lm.fit_CTQ)
```

Association of a random subject's dependent measure scores and corresponding narrative note.

mood and anxiety group:

```{r}
rand_subject <- 52
cat("A random narrative note:\n\n" ,as.character(Narratives_M.A[rand_subject, 2])) 
temp_M.A <- MeasrdScore_M.A[rand_subject, ]
cat("Subjectivity Score:", temp_M.A$sub_score, temp_M.A$sub_score_norm, temp_M.A$sub_score_totalNorm,"\n\nSubjectivity Words:", as.character(temp_M.A$sub_words))
cat("Positive Score:", temp_M.A$pos_score, temp_M.A$pos_score_norm, temp_M.A$pos_score_totalNorm,"\n\nPositive Words:", as.character(temp_M.A$pos_words))
cat("Negative Score:", temp_M.A$neg_score, temp_M.A$neg_score_norm, temp_M.A$neg_score_totalNorm,"\n\nNegative Words:", as.character(temp_M.A$neg_words))
```

healthy control:

```{r}
rand_subject <- 4
cat("A random narrative note:\n\n" ,as.character(Narratives_H[rand_subject, 2])) 
temp_H <- MeasrdScore_H[rand_subject, ]
cat("Subjectivity Score:", temp_H$sub_score,temp_H$sub_score_norm, temp_H$sub_score_totalNorm,"\n\nSubjectivity Words:", as.character(temp_H$sub_words))
cat("Positive Score:", temp_H$pos_score,temp_H$pos_score_norm, temp_H$pos_score_totalNorm, "\n\nPositive Words:", as.character(temp_H$pos_words))
cat("Negative Score:", temp_H$neg_score, temp_H$neg_score_norm, temp_H$neg_score_totalNorm, "\n\nNegative Words:", as.character(temp_H$neg_words))
```

Distributional characteristics in mood/anxiety group

```{r fig.width=8, fig.height=6}
par(mfrow = c(3, 2))
# subjectivity score
hist(MeasrdScore_M.A$sub_score, main= "Histogram of Subjectivity Scores",xlab="Subjectivity Scores")
hist(MeasrdScore_M.A$sub_score, prob = T, main = "Distributional Characteristics", xlab="Subjectivity Scores")
curve(dnorm(x, mean=mean(MeasrdScore_M.A$sub_score), sd=sd(MeasrdScore_M.A$sub_score)), add = TRUE)
abline(v = temp_M.A$sub_score, col = "red", lwd = 2)
# positive score
hist(MeasrdScore_M.A$pos_score, main = "Histogram of Positive Scores" ,xlab="Positive Score")
hist(MeasrdScore_M.A$pos_score, prob = T, main = "Distributional Characteristics", xlab="Positive Scores")
curve(dnorm(x, mean=mean(MeasrdScore_M.A$pos_score), sd=sd(MeasrdScore_M.A$pos_score)), add = TRUE)
abline(v = temp_M.A$pos_score, col = "red", lwd = 2)
# negative score
hist(MeasrdScore_M.A$neg_score, main= "Histogram of Negative Scores",xlab = "Negative Score")
hist(MeasrdScore_M.A$neg_score, prob = T, main = "Distributional Characteristics", xlab = "Negative Scores")
curve(dnorm(x, mean=mean(MeasrdScore_M.A$neg_score), sd=sd(MeasrdScore_M.A$neg_score)), add = TRUE)
abline(v = temp_M.A$neg_score, col = "red", lwd = 2)
```

Distributional characteristics in healthy control group

```{r fig.width=8, fig.height=6}
par(mfrow = c(3, 2))
# subjectivity score
hist(MeasrdScore_H$sub_score, main= "Histogram of Subjectivity Scores",xlab="Subjectivity Scores")
hist(MeasrdScore_H$sub_score, prob = T, main = "Distributional Characteristics", xlab="Subjectivity Scores")
curve(dnorm(x, mean=mean(MeasrdScore_H$sub_score), sd=sd(MeasrdScore_H$sub_score)), add = TRUE)
abline(v = temp_H$sub_score, col = "red", lwd = 2)
# positive score
hist(MeasrdScore_H$pos_score, main = "Histogram of Positive Scores" ,xlab="Positive Score")
hist(MeasrdScore_H$pos_score, prob = T, main = "Distributional Characteristics", xlab="Positive Scores")
curve(dnorm(x, mean=mean(MeasrdScore_H$pos_score), sd=sd(MeasrdScore_H$pos_score)), add = TRUE)
abline(v = temp_H$pos_score, col = "red", lwd = 2)
# negative score
hist(MeasrdScore_H$neg_score, main= "Histogram of Negative Scores",xlab = "Negative Score")
hist(MeasrdScore_H$neg_score, prob = T, main = "Distributional Characteristics", xlab = "Negative Scores")
curve(dnorm(x, mean=mean(MeasrdScore_H$neg_score), sd=sd(MeasrdScore_H$neg_score)), add = TRUE)
abline(v = temp_H$neg_score, col = "red", lwd = 2)
```

Correlation between dependend measure scores

```{r}
library(psych)
pairs.panels(MeasrdScore_M.A[c(2, 7, 12)], main = "mood and anxiety")
pairs.panels(MeasrdScore_H[c(2, 7, 12)], main = "healthy control")
```

Extract Age, Gender, Income, and Education.

```{r}
# mood/anxiety:
Age_M.A    <- SelfReport_M.A[, grep("Age", names(SelfReport_M.A), fixed = T)]
Gender_M.A <- as.vector(SelfReport_M.A[, grep("Gender", names(SelfReport_M.A), fixed = T)])
Edu_M.A    <- SelfReport_M.A[, grep("Education", names(SelfReport_M.A), fixed = T)]
Income_M.A <- SelfReport_M.A[, grep("Income", names(SelfReport_M.A), fixed = T)]
# Assign dependent measures
Sub.score_M.A <- MeasrdScore_M.A$sub_score
Pos.score_M.A <- MeasrdScore_M.A$pos_score
Neg.score_M.A <- MeasrdScore_M.A$neg_score
# healthy control:
Age_H    <- SelfReport_H[, grep("Age", names(SelfReport_H), fixed = T)]
Gender_H <- as.vector(SelfReport_H[, grep("Gender", names(SelfReport_H), fixed = T)])
Edu_H    <- SelfReport_H[, grep("Education", names(SelfReport_H), fixed = T)]
Income_H <- SelfReport_H[, grep("Income", names(SelfReport_H), fixed = T)]
# Assign dependent measures
Sub.score_H <- MeasrdScore_H$sub_score
Pos.score_H <- MeasrdScore_H$pos_score
Neg.score_H <- MeasrdScore_H$neg_score
```

Determine the degree to which socio-demographic characteristics effect the dependent measures.

mood/anxiety group:

```{r fig.width=10, fig.height=7}
# Subjectivity score as dependent measure
par(mfrow = c(3, 4))
lm.fit_age <- lm(Sub.score_M.A ~ Age_M.A)
plot(Age_M.A, Sub.score_M.A, main = "effect of age", xlab = "Age", ylab = "Subjectivity score")
abline(lm.fit_age)
lm.fit_gender <- lm(Sub.score_M.A ~ Gender_M.A)
plot(Gender_M.A, Sub.score_M.A, main = "effect of gender", xlab = "Gender", ylab = "Subjectivity score")
abline(lm.fit_gender)
lm.fit_edu <- lm(Sub.score_M.A ~ Edu_M.A)
plot(Edu_M.A, Sub.score_M.A, main = "effect of education", xlab = "Education", ylab = "Subjectivity score")
abline(lm.fit_edu)
lm.fit_inc <- lm(Sub.score_M.A ~ Income_M.A)
plot(Income_M.A, Sub.score_M.A, main = "effect of income", xlab = "Income", ylab = "Subjectivity score")
abline(lm.fit_inc)
# Positive score  as dependent measure
lm.fit_age <- lm(Pos.score_M.A ~ Age_M.A)
plot(Age_M.A, Pos.score_M.A, main = "effect of age", xlab = "Age", ylab = "positive score")
abline(lm.fit_age)
lm.fit_gender <- lm(Pos.score_M.A ~ Gender_M.A)
plot(Gender_M.A, Pos.score_M.A, main = "effect of gender", xlab = "Gender", ylab = "positive score")
abline(lm.fit_gender)
lm.fit_edu <- lm(Pos.score_M.A ~ Edu_M.A)
plot(Edu_M.A, Pos.score_M.A, main = "effect of education", xlab = "Education", ylab = "positive score")
abline(lm.fit_edu)
lm.fit_inc <- lm(Pos.score_M.A ~ Income_M.A)
plot(Income_M.A, Pos.score_M.A, main = "effect of income", xlab = "Income", ylab = "positive score")
abline(lm.fit_inc)
# Negative score  as dependent measure
lm.fit_age <- lm(Neg.score_M.A ~ Age_M.A)
plot(Age_M.A, Neg.score_M.A, main = "effect of age", xlab = "Age", ylab = "negative score")
abline(lm.fit_age)
lm.fit_gender <- lm(Neg.score_M.A ~ Gender_M.A)
plot(Gender_M.A, Neg.score_M.A, main = "effect of gender ", xlab = "Gender", ylab = "negative score")
abline(lm.fit_gender)
lm.fit_edu <- lm(Neg.score_M.A ~ Edu_M.A)
plot(Edu_M.A, Neg.score_M.A, main = "effect of education", xlab = "Education", ylab = "negative score")
abline(lm.fit_edu)
lm.fit_inc <- lm(Neg.score_M.A ~ Income_M.A)
plot(Income_M.A, Neg.score_M.A, main = "effect of income", xlab = "Income", ylab = "negative score")
abline(lm.fit_inc)
```

healthy control group:

```{r fig.width=10, fig.height=7}
# Subjectivity score as dependent measure
par(mfrow = c(3, 4))
lm.fit_age <- lm(Sub.score_H ~ Age_H)
plot(Age_H, Sub.score_H, main = "effect of age", xlab = "Age", ylab = "Subjectivity score")
abline(lm.fit_age)
lm.fit_gender <- lm(Sub.score_H ~ Gender_H)
plot(Gender_H, Sub.score_H, main = "effect of gender", xlab = "Gender", ylab = "Subjectivity score")
abline(lm.fit_gender)
lm.fit_edu <- lm(Sub.score_H ~ Edu_H)
plot(Edu_H, Sub.score_H, main = "effect of education", xlab = "Education", ylab = "Subjectivity score")
abline(lm.fit_edu)
lm.fit_inc <- lm(Sub.score_H ~ Income_H)
plot(Income_H, Sub.score_H, main = "effect of income", xlab = "Income", ylab = "Subjectivity score")
abline(lm.fit_inc)
# Positive score  as dependent measure
lm.fit_age <- lm(Pos.score_H ~ Age_H)
plot(Age_H, Pos.score_H, main = "effect of age", xlab = "Age", ylab = "positive score")
abline(lm.fit_age)
lm.fit_gender <- lm(Pos.score_H ~ Gender_H)
plot(Gender_H, Pos.score_H, main = "effect of gender", xlab = "Gender", ylab = "positive score")
abline(lm.fit_gender)
lm.fit_edu <- lm(Pos.score_H ~ Edu_H)
plot(Edu_H, Pos.score_H, main = "effect of education", xlab = "Education", ylab = "positive score")
abline(lm.fit_edu)
lm.fit_inc <- lm(Pos.score_H ~ Income_H)
plot(Income_H, Pos.score_H, main = "effect of income", xlab = "Income", ylab = "positive score")
abline(lm.fit_inc)
# Negative score  as dependent measure
lm.fit_age <- lm(Neg.score_H ~ Age_H)
plot(Age_H, Neg.score_H, main = "effect of age", xlab = "Age", ylab = "negative score")
abline(lm.fit_age)
lm.fit_gender <- lm(Neg.score_H ~ Gender_H)
plot(Gender_H, Neg.score_H, main = "effect of gender ", xlab = "Gender", ylab = "negative score")
abline(lm.fit_gender)
lm.fit_edu <- lm(Neg.score_H ~ Edu_H)
plot(Edu_H, Neg.score_H, main = "effect of education", xlab = "Education", ylab = "negative score")
abline(lm.fit_edu)
lm.fit_inc <- lm(Neg.score_H ~ Income_H)
plot(Income_H, Neg.score_H, main = "effect of income", xlab = "Income", ylab = "negative score")
abline(lm.fit_inc)
```

Determine the relationship with respect to the following trait variables:
(PANAS-X, BIF, Symptom scales PHQ-9)

mood/anxiety group:

```{r fig.width=8, fig.height=7}
PANASX_pos_M.A <- SelfReport_M.A[ ,grepl("PANASX_PosAffect", names(SelfReport_M.A))]
PANASX_neg_M.A <- SelfReport_M.A[ ,grepl("PANASX_NegAffect", names(SelfReport_M.A))]
PHQ_M.A <- SelfReport_M.A$PHQ

# Subjectivity score as dependent measure
par(mfrow = c(3, 3))
lm_fit_PAN.pos <- lm(Sub.score_M.A ~ PANASX_pos_M.A)
plot(PANASX_pos_M.A, Sub.score_M.A, main = "effect of PANASX positive", xlab = "PANASX positive", ylab = "Subjectivity score")
abline(lm_fit_PAN.pos)

lm_fit_PAN.neg <- lm(Sub.score_M.A ~ PANASX_neg_M.A)
plot(PANASX_neg_M.A, Sub.score_M.A, main = "effect of PANASX negative", xlab = "PANASX negative", ylab = "Subjectivity score")
abline(lm_fit_PAN.neg)

lm_fit_PHQ <- lm(Sub.score_M.A ~ PHQ_M.A)
plot(PHQ_M.A, Sub.score_M.A, main = "effect of PHQ", xlab = "PHQ", ylab = "Subjectivity score")
abline(lm_fit_PHQ)

# Positive score as dependent measure
lm_fit_PAN.pos <- lm(Pos.score_M.A ~ PANASX_pos_M.A)
plot(PANASX_pos_M.A, Pos.score_M.A, main = "effect of PANASX positive", xlab = "PANASX positive", ylab = "Positive score")
abline(lm_fit_PAN.pos)

lm_fit_PAN.neg <- lm(Pos.score_M.A ~ PANASX_neg_M.A)
plot(PANASX_neg_M.A, Pos.score_M.A, main = "effect of PANASX negative", xlab = "PANASX negative", ylab = "Positive score")
abline(lm_fit_PAN.neg)

lm_fit_PHQ <- lm(Pos.score_M.A ~ PHQ_M.A)
plot(PHQ_M.A, Pos.score_M.A, main = "effect of PHQ", xlab = "PHQ", ylab = "Positive score")
abline(lm_fit_PHQ)

# Negative score as dependent measure
lm_fit_PAN.pos <- lm(Neg.score_M.A ~ PANASX_pos_M.A)
plot(PANASX_pos_M.A, Neg.score_M.A, main = "effect of PANASX positive", xlab = "PANASX positive", ylab = "Negative score")
abline(lm_fit_PAN.pos)

lm_fit_PAN.neg <- lm(Neg.score_M.A ~ PANASX_neg_M.A)
plot(PANASX_neg_M.A, Neg.score_M.A, main = "effect of PANASX negative", xlab = "PANASX negative", ylab = "Negative score")
abline(lm_fit_PAN.neg)

lm_fit_PHQ <- lm(Neg.score_M.A ~ PHQ_M.A)
plot(PHQ_M.A, Neg.score_M.A, main = "effect of PHQ", xlab = "PHQ", ylab = "Negative score")
abline(lm_fit_PHQ)
```

healthy control group:

```{r fig.width=8, fig.height=7}
PANASX_pos_H <- SelfReport_H[ ,grepl("PANASX_PosAffect", names(SelfReport_H))]
PANASX_neg_H <- SelfReport_H[ ,grepl("PANASX_NegAffect", names(SelfReport_H))]
PHQ_H <- SelfReport_H$PHQ

# Subjectivity score as dependent measure
par(mfrow = c(3, 3))
lm_fit_PAN.pos <- lm(Sub.score_H ~ PANASX_pos_H)
plot(PANASX_pos_H, Sub.score_H, main = "effect of PANASX positive", xlab = "PANASX positive", ylab = "Subjectivity score")
abline(lm_fit_PAN.pos)

lm_fit_PAN.neg <- lm(Sub.score_H ~ PANASX_neg_H)
plot(PANASX_neg_H, Sub.score_H, main = "effect of PANASX negative", xlab = "PANASX negative", ylab = "Subjectivity score")
abline(lm_fit_PAN.neg)

lm_fit_PHQ <- lm(Sub.score_H ~ PHQ_H)
plot(PHQ_H, Sub.score_H, main = "effect of PHQ", xlab = "PHQ", ylab = "Subjectivity score")
abline(lm_fit_PHQ)

# Positive score as dependent measure
lm_fit_PAN.pos <- lm(Pos.score_H ~ PANASX_pos_H)
plot(PANASX_pos_H, Pos.score_H, main = "effect of PANASX positive", xlab = "PANASX positive", ylab = "Positive score")
abline(lm_fit_PAN.pos)

lm_fit_PAN.neg <- lm(Pos.score_H ~ PANASX_neg_H)
plot(PANASX_neg_H, Pos.score_H, main = "effect of PANASX negative", xlab = "PANASX negative", ylab = "Positive score")
abline(lm_fit_PAN.neg)

lm_fit_PHQ <- lm(Pos.score_H ~ PHQ_H)
plot(PHQ_H, Pos.score_H, main = "effect of PHQ", xlab = "PHQ", ylab = "Positive score")
abline(lm_fit_PHQ)

# Negative score as dependent measure
lm_fit_PAN.pos <- lm(Neg.score_H ~ PANASX_pos_H)
plot(PANASX_pos_H, Neg.score_H, main = "effect of PANASX positive", xlab = "PANASX positive", ylab = "Negative score")
abline(lm_fit_PAN.pos)

lm_fit_PAN.neg <- lm(Neg.score_H ~ PANASX_neg_H)
plot(PANASX_neg_H, Neg.score_H, main = "effect of PANASX negative", xlab = "PANASX negative", ylab = "Negative score")
abline(lm_fit_PAN.neg)

lm_fit_PHQ <- lm(Neg.score_H ~ PHQ_H)
plot(PHQ_H, Neg.score_H, main = "effect of PHQ", xlab = "PHQ", ylab = "Negative score")
abline(lm_fit_PHQ)
```

Determine the effect of BFI on Dependent measures:

Mood and anxiety:

```{r fig.width=10, fig.height=7}
BFI_con_M.A <- SelfReport_M.A[ ,grepl("BFI_Conscious", names(SelfReport_M.A))]
BFI_open_M.A <- SelfReport_M.A[ ,grepl("BFI_Openness", names(SelfReport_M.A))]
BFI_agree_M.A <- SelfReport_M.A[ ,grepl("BFI_Agreeb", names(SelfReport_M.A))]
BFI_extrav_M.A <- SelfReport_M.A[ ,grepl("BFI_Extrav", names(SelfReport_M.A))]
BFI_neurot_M.A <- SelfReport_M.A[ ,grepl("BFI_Neurot", names(SelfReport_M.A))]

# Subjectivity score as dependent measure
par(mfrow = c(3, 5))
lm_fit_BFI.con <- lm(Sub.score_M.A ~ BFI_con_M.A)
plot(BFI_con_M.A, Sub.score_M.A, main = "effect of BFI conscious", xlab = "BFI conscious", ylab = "Subjectivity score")
abline(lm_fit_BFI.con)

lm_fit_BFI.open <- lm(Sub.score_M.A ~ BFI_open_M.A)
plot(BFI_open_M.A, Sub.score_M.A, main = "effect of BFI openness", xlab = "BFI openness", ylab = "Subjectivity score")
abline(lm_fit_BFI.open)

lm_fit_BFI.agree <- lm(Sub.score_M.A ~ BFI_agree_M.A)
plot(BFI_agree_M.A, Sub.score_M.A, main = "effect of BFI Agreeb", xlab = "BFI Agreeb", ylab = "Subjectivity score")
abline(lm_fit_BFI.agree)

lm_fit_BFI.extrav <- lm(Sub.score_M.A ~ BFI_extrav_M.A)
plot(BFI_extrav_M.A, Sub.score_M.A, main = "effect of BFI Extrav", xlab = "BFI Extrav", ylab = "Subjectivity score")
abline(lm_fit_BFI.extrav)

lm_fit_BFI.neurot <- lm(Sub.score_M.A ~ BFI_neurot_M.A)
plot(BFI_neurot_M.A, Sub.score_M.A, main = "effect of BFI Neurot", xlab = "BFI Neurot", ylab = "Subjectivity score")
abline(lm_fit_BFI.neurot)
# Positive score as dependent measure
lm_fit_BFI.con <- lm(Pos.score_M.A ~ BFI_con_M.A)
plot(BFI_con_M.A, Pos.score_M.A, main = "effect of BFI conscious", xlab = "BFI conscious", ylab = "Positive score")
abline(lm_fit_BFI.con)

lm_fit_BFI.open <- lm(Pos.score_M.A ~ BFI_open_M.A)
plot(BFI_open_M.A, Pos.score_M.A, main = "effect of BFI openness", xlab = "BFI openness", ylab = "Positive score")
abline(lm_fit_BFI.open)

lm_fit_BFI.agree <- lm(Pos.score_M.A ~ BFI_agree_M.A)
plot(BFI_agree_M.A, Pos.score_M.A, main = "effect of BFI Agreeb", xlab = "BFI Agreeb", ylab = "Positive score")
abline(lm_fit_BFI.agree)

lm_fit_BFI.extrav <- lm(Pos.score_M.A ~ BFI_extrav_M.A)
plot(BFI_extrav_M.A, Pos.score_M.A, main = "effect of BFI Extrav", xlab = "BFI Extrav", ylab = "Positive score")
abline(lm_fit_BFI.extrav)

lm_fit_BFI.neurot <- lm(Pos.score_M.A ~ BFI_neurot_M.A)
plot(BFI_neurot_M.A, Pos.score_M.A, main = "effect of BFI Neurot", xlab = "BFI Neurot", ylab = "Positive score")
abline(lm_fit_BFI.neurot)
# Negative score as dependent measure
lm_fit_BFI.con <- lm(Neg.score_M.A ~ BFI_con_M.A)
plot(BFI_con_M.A, Neg.score_M.A, main = "effect of BFI conscious", xlab = "BFI conscious", ylab = "Negative score")
abline(lm_fit_BFI.con)

lm_fit_BFI.open <- lm(Neg.score_M.A ~ BFI_open_M.A)
plot(BFI_open_M.A, Neg.score_M.A, main = "effect of BFI openness", xlab = "BFI openness", ylab = "Negative score")
abline(lm_fit_BFI.open)

lm_fit_BFI.agree <- lm(Neg.score_M.A ~ BFI_agree_M.A)
plot(BFI_agree_M.A, Neg.score_M.A, main = "effect of BFI Agreeb", xlab = "BFI Agreeb", ylab = "Negative score")
abline(lm_fit_BFI.agree)

lm_fit_BFI.extrav <- lm(Neg.score_M.A ~ BFI_extrav_M.A)
plot(BFI_extrav_M.A, Neg.score_M.A, main = "effect of BFI Extrav", xlab = "BFI Extrav", ylab = "Negative score")
abline(lm_fit_BFI.extrav)

lm_fit_BFI.neurot <- lm(Neg.score_M.A ~ BFI_neurot_M.A)
plot(BFI_neurot_M.A, Neg.score_M.A, main = "effect of BFI Neurot", xlab = "BFI Neurot", ylab = "Negative score")
abline(lm_fit_BFI.neurot)
```

healthy control:

```{r fig.width=10, fig.height=7}
BFI_con_H <- SelfReport_H[ ,grepl("BFI_Conscious", names(SelfReport_H))]
BFI_open_H <- SelfReport_H[ ,grepl("BFI_Openness", names(SelfReport_H))]
BFI_agree_H <- SelfReport_H[ ,grepl("BFI_Agreeb", names(SelfReport_H))]
BFI_extrav_H <- SelfReport_H[ ,grepl("BFI_Extrav", names(SelfReport_H))]
BFI_neurot_H <- SelfReport_H[ ,grepl("BFI_Neurot", names(SelfReport_H))]


# Subjectivity score as dependent measure
par(mfrow = c(3, 5))
lm_fit_BFI.con <- lm(Sub.score_H ~ BFI_con_H)
plot(BFI_con_H, Sub.score_H, main = "effect of BFI conscious", xlab = "BFI conscious", ylab = "Subjectivity score")
abline(lm_fit_BFI.con)

lm_fit_BFI.open <- lm(Sub.score_H ~ BFI_open_H)
plot(BFI_open_H, Sub.score_H, main = "effect of BFI openness", xlab = "BFI openness", ylab = "Subjectivity score")
abline(lm_fit_BFI.open)

lm_fit_BFI.agree <- lm(Sub.score_H ~ BFI_agree_H)
plot(BFI_agree_H, Sub.score_H, main = "effect of BFI Agreeb", xlab = "BFI Agreeb", ylab = "Subjectivity score")
abline(lm_fit_BFI.agree)

lm_fit_BFI.extrav <- lm(Sub.score_H ~ BFI_extrav_H)
plot(BFI_extrav_H, Sub.score_H, main = "effect of BFI Extrav", xlab = "BFI Extrav", ylab = "Subjectivity score")
abline(lm_fit_BFI.extrav)

lm_fit_BFI.neurot <- lm(Sub.score_H ~ BFI_neurot_H)
plot(BFI_neurot_H, Sub.score_H, main = "effect of BFI Neurot", xlab = "BFI Neurot", ylab = "Subjectivity score")
abline(lm_fit_BFI.neurot)


# Positive score as dependent measure
lm_fit_BFI.con <- lm(Pos.score_H ~ BFI_con_H)
plot(BFI_con_H, Pos.score_H, main = "effect of BFI conscious", xlab = "BFI conscious", ylab = "Positive score")
abline(lm_fit_BFI.con)

lm_fit_BFI.open <- lm(Pos.score_H ~ BFI_open_H)
plot(BFI_open_H, Pos.score_H, main = "effect of BFI openness", xlab = "BFI openness", ylab = "Positive score")
abline(lm_fit_BFI.open)

lm_fit_BFI.agree <- lm(Pos.score_H ~ BFI_agree_H)
plot(BFI_agree_H, Pos.score_H, main = "effect of BFI Agreeb", xlab = "BFI Agreeb", ylab = "Positive score")
abline(lm_fit_BFI.agree)

lm_fit_BFI.extrav <- lm(Pos.score_H ~ BFI_extrav_H)
plot(BFI_extrav_H, Pos.score_H, main = "effect of BFI Extrav", xlab = "BFI Extrav", ylab = "Positive score")
abline(lm_fit_BFI.extrav)

lm_fit_BFI.neurot <- lm(Pos.score_H ~ BFI_neurot_H)
plot(BFI_neurot_H, Pos.score_H, main = "effect of BFI Neurot", xlab = "BFI Neurot", ylab = "Positive score")
abline(lm_fit_BFI.neurot)


# Negative score as dependent measure
lm_fit_BFI.con <- lm(Neg.score_H ~ BFI_con_H)
plot(BFI_con_H, Neg.score_H, main = "effect of BFI conscious", xlab = "BFI conscious", ylab = "Negative score")
abline(lm_fit_BFI.con)

lm_fit_BFI.open <- lm(Neg.score_H ~ BFI_open_H)
plot(BFI_open_H, Neg.score_H, main = "effect of BFI openness", xlab = "BFI openness", ylab = "Negative score")
abline(lm_fit_BFI.open)

lm_fit_BFI.agree <- lm(Neg.score_H ~ BFI_agree_H)
plot(BFI_agree_H, Neg.score_H, main = "effect of BFI Agreeb", xlab = "BFI Agreeb", ylab = "Negative score")
abline(lm_fit_BFI.agree)

lm_fit_BFI.extrav <- lm(Neg.score_H ~ BFI_extrav_H)
plot(BFI_extrav_H, Neg.score_H, main = "effect of BFI Extrav", xlab = "BFI Extrav", ylab = "Negative score")
abline(lm_fit_BFI.extrav)

lm_fit_BFI.neurot <- lm(Neg.score_H ~ BFI_neurot_H)
plot(BFI_neurot_H, Neg.score_H, main = "effect of BFI Neurot", xlab = "BFI Neurot", ylab = "Negative score")
abline(lm_fit_BFI.neurot)
```


Determine the relationship with respect to the following trait variables:
(Symptom scales OASIS), PROMIS (anxiety, depression, anger), Interviewers)

mood and anxiety group:

```{r fig.width=10, fig.height=7}
OASIS_M.A <- SelfReport_M.A$OASIS
PROMIS.Ang_M.A <- SelfReport_M.A[ ,grepl("PROMIS_AngerTscore", names(SelfReport_M.A))]
PROMIS.Dep_M.A <- SelfReport_M.A[ , grepl("PROMIS_DepressTscore", names(SelfReport_M.A))]
PROMIS_Anx_M.A <- SelfReport_M.A[ , grepl("PROMIS_AnxietyTscore", names(SelfReport_M.A))]
LC_M.A <- as.numeric(Narratives_M.A$LC_conducted_by)
# Subjectivity score as dependent measure
par(mfrow = c(3, 5))
lm_fit_OASIS <- lm(Sub.score_M.A ~ OASIS_M.A)
plot(OASIS_M.A, Sub.score_M.A, main = "effect of OASIS", xlab = "OASIS", ylab = "Subjectivity score")
abline(lm_fit_OASIS)
lm_fit_PROMIS.Ang <- lm(Sub.score_M.A ~ PROMIS.Ang_M.A)
plot(PROMIS.Ang_M.A, Sub.score_M.A, main = "effect of PROMIS Anger", xlab = "PROMIS Anger", ylab = "Subjectivity score")
abline(lm_fit_PROMIS.Ang)
lm_fit_PROMIS.Dep <- lm(Sub.score_M.A ~ PROMIS.Dep_M.A)
plot(PROMIS.Dep_M.A, Sub.score_M.A, main = "effect of PROMIS Depress", xlab = "PROMIS Depress", ylab = "Subjectivity score")
abline(lm_fit_PROMIS.Dep)
lm_fit_PROMIS_Anx <- lm(Sub.score_M.A ~ PROMIS_Anx_M.A)
plot(PROMIS_Anx_M.A, Sub.score_M.A, main = "effect of PROMIS Anxiety", xlab = "PROMIS Anxiety", ylab = "Subjectivity score")
abline(lm_fit_PROMIS_Anx)
lm_fit_LC <- lm(Sub.score_M.A ~ LC_M.A)
plot(LC_M.A, Sub.score_M.A, main = "effect of LC", xlab = "LC", ylab = "Subjectivity score")
abline(lm_fit_LC)
# Positive score as dependent measure
lm_fit_OASIS <- lm(Pos.score_M.A ~ OASIS_M.A)
plot(OASIS_M.A, Pos.score_M.A, main = "effect of OASIS", xlab = "OASIS", ylab = "Positive score")
abline(lm_fit_OASIS)
lm_fit_PROMIS.Ang <- lm(Pos.score_M.A ~ PROMIS.Ang_M.A)
plot(PROMIS.Ang_M.A, Pos.score_M.A, main = "effect of PROMIS Anger", xlab = "PROMIS Anger", ylab = "Positive score")
abline(lm_fit_PROMIS.Ang)
lm_fit_PROMIS.Dep <- lm(Pos.score_M.A ~ PROMIS.Dep_M.A)
plot(PROMIS.Dep_M.A, Pos.score_M.A, main = "effect of PROMIS Depress", xlab = "PROMIS Depress", ylab = "Positive score")
abline(lm_fit_PROMIS.Dep)
lm_fit_PROMIS_Anx <- lm(Pos.score_M.A ~ PROMIS_Anx_M.A)
plot(PROMIS_Anx_M.A, Pos.score_M.A, main = "effect of PROMIS Anxiety", xlab = "PROMIS Anxiety", ylab = "Positive score")
abline(lm_fit_PROMIS_Anx)
lm_fit_LC <- lm(Pos.score_M.A ~ LC_M.A)
plot(LC_M.A, Pos.score_M.A, main = "effect of LC", xlab = "LC", ylab = "Positive score")
abline(lm_fit_LC)
# Negative score as dependent measure
lm_fit_OASIS <- lm(Neg.score_M.A ~ OASIS_M.A)
plot(OASIS_M.A, Neg.score_M.A, main = "effect of OASIS", xlab = "OASIS", ylab = "Negative score")
abline(lm_fit_OASIS)
lm_fit_PROMIS.Ang <- lm(Neg.score_M.A ~ PROMIS.Ang_M.A)
plot(PROMIS.Ang_M.A, Neg.score_M.A, main = "effect of PROMIS Anger", xlab = "PROMIS Anger", ylab = "Negative score")
abline(lm_fit_PROMIS.Ang)
lm_fit_PROMIS.Dep <- lm(Neg.score_M.A ~ PROMIS.Dep_M.A)
plot(PROMIS.Dep_M.A, Neg.score_M.A, main = "effect of PROMIS Depress", xlab = "PROMIS Depress", ylab = "Negative score")
abline(lm_fit_PROMIS.Dep)
lm_fit_PROMIS_Anx <- lm(Neg.score_M.A ~ PROMIS_Anx_M.A)
plot(PROMIS_Anx_M.A, Neg.score_M.A, main = "effect of PROMIS Anxiety", xlab = "PROMIS Anxiety", ylab = "Negative score")
abline(lm_fit_PROMIS_Anx)
lm_fit_LC <- lm(Neg.score_M.A ~ LC_M.A)
plot(LC_M.A, Neg.score_M.A, main = "effect of LC", xlab = "LC", ylab = "Negative score")
abline(lm_fit_LC)
```

healthy control group:

```{r fig.width=10, fig.height=7}
OASIS_H <- SelfReport_H$OASIS
PROMIS.Ang_H <- SelfReport_H[ ,grepl("PROMIS_AngerTscore", names(SelfReport_H))]
PROMIS.Dep_H <- SelfReport_H[ , grepl("PROMIS_DepressTscore", names(SelfReport_H))]
PROMIS_Anx_H <- SelfReport_H[ , grepl("PROMIS_AnxietyTscore", names(SelfReport_H))]
LC_H <- as.numeric(Narratives_H$LC_conducted_by)
# Subjectivity score as dependent measure
par(mfrow = c(3, 5))
lm_fit_OASIS <- lm(Sub.score_H ~ OASIS_H)
plot(OASIS_H, Sub.score_H, main = "effect of OASIS", xlab = "OASIS", ylab = "Subjectivity score")
abline(lm_fit_OASIS)
lm_fit_PROMIS.Ang <- lm(Sub.score_H ~ PROMIS.Ang_H)
plot(PROMIS.Ang_H, Sub.score_H, main = "effect of PROMIS Anger", xlab = "PROMIS Anger", ylab = "Subjectivity score")
abline(lm_fit_PROMIS.Ang)
lm_fit_PROMIS.Dep <- lm(Sub.score_H ~ PROMIS.Dep_H)
plot(PROMIS.Dep_H, Sub.score_H, main = "effect of PROMIS Depress", xlab = "PROMIS Depress", ylab = "Subjectivity score")
abline(lm_fit_PROMIS.Dep)
lm_fit_PROMIS_Anx <- lm(Sub.score_H ~ PROMIS_Anx_H)
plot(PROMIS_Anx_H, Sub.score_H, main = "effect of PROMIS Anxiety", xlab = "PROMIS Anxiety", ylab = "Subjectivity score")
abline(lm_fit_PROMIS_Anx)
lm_fit_LC <- lm(Sub.score_H ~ LC_H)
plot(LC_H, Sub.score_H, main = "effect of LC", xlab = "LC", ylab = "Subjectivity score")
abline(lm_fit_LC)
# Positive score as dependent measure
lm_fit_OASIS <- lm(Pos.score_H ~ OASIS_H)
plot(OASIS_H, Pos.score_H, main = "effect of OASIS", xlab = "OASIS", ylab = "Positive score")
abline(lm_fit_OASIS)
lm_fit_PROMIS.Ang <- lm(Pos.score_H ~ PROMIS.Ang_H)
plot(PROMIS.Ang_H, Pos.score_H, main = "effect of PROMIS Anger", xlab = "PROMIS Anger", ylab = "Positive score")
abline(lm_fit_PROMIS.Ang)
lm_fit_PROMIS.Dep <- lm(Pos.score_H ~ PROMIS.Dep_H)
plot(PROMIS.Dep_H, Pos.score_H, main = "effect of PROMIS Depress", xlab = "PROMIS Depress", ylab = "Positive score")
abline(lm_fit_PROMIS.Dep)
lm_fit_PROMIS_Anx <- lm(Pos.score_H ~ PROMIS_Anx_H)
plot(PROMIS_Anx_H, Pos.score_H, main = "effect of PROMIS Anxiety", xlab = "PROMIS Anxiety", ylab = "Positive score")
abline(lm_fit_PROMIS_Anx)
lm_fit_LC <- lm(Pos.score_H ~ LC_H)
plot(LC_H, Pos.score_H, main = "effect of LC", xlab = "LC", ylab = "Positive score")
abline(lm_fit_LC)
# Negative score as dependent measure
lm_fit_OASIS <- lm(Neg.score_H ~ OASIS_H)
plot(OASIS_H, Neg.score_H, main = "effect of OASIS", xlab = "OASIS", ylab = "Negative score")
abline(lm_fit_OASIS)
lm_fit_PROMIS.Ang <- lm(Neg.score_H ~ PROMIS.Ang_H)
plot(PROMIS.Ang_H, Neg.score_H, main = "effect of PROMIS Anger", xlab = "PROMIS Anger", ylab = "Negative score")
abline(lm_fit_PROMIS.Ang)
lm_fit_PROMIS.Dep <- lm(Neg.score_H ~ PROMIS.Dep_H)
plot(PROMIS.Dep_H, Neg.score_H, main = "effect of PROMIS Depress", xlab = "PROMIS Depress", ylab = "Negative score")
abline(lm_fit_PROMIS.Dep)
lm_fit_PROMIS_Anx <- lm(Neg.score_H ~ PROMIS_Anx_H)
plot(PROMIS_Anx_H, Neg.score_H, main = "effect of PROMIS Anxiety", xlab = "PROMIS Anxiety", ylab = "Negative score")
abline(lm_fit_PROMIS_Anx)
lm_fit_LC <- lm(Neg.score_H ~ LC_H)
plot(LC_H, Neg.score_H, main = "effect of LC", xlab = "LC", ylab = "Negative score")
abline(lm_fit_LC)
```

Determine mediating influences (CTQ, TEC)on dependent measured scores.

```{r}
# mood/anxiety
CTQ_M.A <- SelfReport_M.A[ ,grepl("CTQ_score", names(SelfReport_M.A))]
TES_M.A <- SelfReport_M.A[ ,grepl("TES_TotalOccurrence", names(SelfReport_M.A))]
DAST_M.A <- SelfReport_M.A[ ,grepl("DAST", names(SelfReport_M.A))]
# healthy control
CTQ_H <- SelfReport_H[ ,grepl("CTQ_score", names(SelfReport_H))]
TES_H <- SelfReport_H[ ,grepl("TES_TotalOccurrence", names(SelfReport_H))]
DAST_H <- SelfReport_H[ ,grepl("DAST", names(SelfReport_H))]
```

mood/anxiety:

```{r fig.width=8, fig.height=7}
# Subjectivity score as dependent measure
par(mfrow = c(3, 3))
lm_fit_CTQ <- lm(Sub.score_M.A ~ CTQ_M.A)
plot(CTQ_M.A, Sub.score_M.A, main = "effect of CTQ (mood/anxiety)", xlab = "CTQ", ylab = "Subjectivity score")
abline(lm_fit_CTQ)
lm_fit_TES <- lm(Sub.score_M.A ~ TES_M.A)
plot(TES_M.A, Sub.score_M.A, main = "effect of TES (mood/anxiety)", xlab = "TES", ylab = "Subjectivity score")
abline(lm_fit_TES)
lm_fit_DAST <- lm(Sub.score_M.A ~ DAST_M.A)
plot(DAST_M.A, Sub.score_M.A, main = "effect of DAST (mood/anxiety)", xlab = "DAST", ylab = "Subjectivity score")
abline(lm_fit_DAST)
# Positive score as dependent measure
lm_fit_CTQ <- lm(Pos.score_M.A ~ CTQ_M.A)
plot(CTQ_M.A, Pos.score_M.A, main = "effect of CTQ (mood/anxiety)", xlab = "CTQ", ylab = "Positive score")
abline(lm_fit_CTQ)
lm_fit_TES <- lm(Pos.score_M.A ~ TES_M.A)
plot(TES_M.A, Pos.score_M.A, main = "effect of TES (mood/anxiety)", xlab = "TES", ylab = "Positive score")
abline(lm_fit_TES)
lm_fit_DAST <- lm(Pos.score_M.A ~ DAST_M.A)
plot(DAST_M.A, Pos.score_M.A, main = "effect of DAST (mood/anxiety)", xlab = "DAST", ylab = "Positive score")
abline(lm_fit_DAST)
# Negative score as dependent measure
lm_fit_CTQ <- lm(Neg.score_M.A ~ CTQ_M.A)
plot(CTQ_M.A, Neg.score_M.A, main = "effect of CTQ (mood/anxiety)", xlab = "CTQ", ylab = "Negative score")
abline(lm_fit_CTQ)
lm_fit_TES <- lm(Neg.score_M.A ~ TES_M.A)
plot(TES_M.A, Neg.score_M.A, main = "effect of TES (mood/anxiety)", xlab = "TES", ylab = "Negative score")
abline(lm_fit_TES)
lm_fit_DAST <- lm(Neg.score_M.A ~ DAST_M.A)
plot(DAST_M.A, Neg.score_M.A, main = "effect of DAST (mood/anxiety)", xlab = "DAST", ylab = "Negative score")
abline(lm_fit_DAST)
```

healthy control:

```{r fig.width=8, fig.height=7}
# Subjectivity score as dependent measure
par(mfrow = c(3, 3))
lm_fit_CTQ <- lm(Sub.score_H ~ CTQ_H)
plot(CTQ_H, Sub.score_H, main = "effect of CTQ (healthy control)", xlab = "CTQ", ylab = "Subjectivity score")
abline(lm_fit_CTQ)
lm_fit_TES <- lm(Sub.score_H ~ TES_H)
plot(TES_H, Sub.score_H, main = "effect of TES (healthy control)", xlab = "TES", ylab = "Subjectivity score")
abline(lm_fit_TES)
lm_fit_DAST <- lm(Sub.score_H ~ DAST_H)
plot(DAST_H, Sub.score_H, main = "effect of DAST (healthy control)", xlab = "DAST", ylab = "Subjectivity score")
abline(lm_fit_DAST)
# Positive score as dependent measure
lm_fit_CTQ <- lm(Pos.score_H ~ CTQ_H)
plot(CTQ_H, Pos.score_H, main = "effect of CTQ (healthy control)", xlab = "CTQ", ylab = "Positive score")
abline(lm_fit_CTQ)
lm_fit_TES <- lm(Pos.score_H ~ TES_H)
plot(TES_H, Pos.score_H, main = "effect of TES (healthy control)", xlab = "TES", ylab = "Positive score")
abline(lm_fit_TES)
lm_fit_DAST <- lm(Pos.score_H ~ DAST_H)
plot(DAST_H, Pos.score_H, main = "effect of DAST (healthy control)", xlab = "DAST", ylab = "Positive score")
abline(lm_fit_DAST)
# Negative score as dependent measure
lm_fit_CTQ <- lm(Neg.score_H ~ CTQ_H)
plot(CTQ_H, Neg.score_H, main = "effect of CTQ (healthy control)", xlab = "CTQ", ylab = "Negative score")
abline(lm_fit_CTQ)
lm_fit_TES <- lm(Neg.score_H ~ TES_H)
plot(TES_H, Neg.score_H, main = "effect of TES (healthy control)", xlab = "TES", ylab = "Negative score")
abline(lm_fit_TES)
lm_fit_DAST <- lm(Neg.score_H ~ DAST_H)
plot(DAST_H, Neg.score_H, main = "effect of DAST (healthy control)", xlab = "DAST", ylab = "Negative score")
abline(lm_fit_DAST)
```

