---
title: "Association between dependent measures and T-500 self-reported in Mood/Anxiety"
author: "Saeid Parvandeh"
date: "June 2017"
output: html_document
---
Analysis description:
T-500 self-reported data base consists of many different coded claim data related to each subject and capture only some elements clinical representation, here we measure other benefits from narrative discharge summaries also called lifechart narrative note that is a short story of subject's life. We used a Natural Language Processing method that aggregates words emotion with three scores, word with positive valence (between 0-1), word with negative valence (between -1-0), and degree of word subjectivity (between 0-1). In this analysis study, we compute three scores for each subject and investigate the association between the measured scores and T-500 data, based on mood/axiety group, step-by-step.

Number of subjects in mood/axiety.

```{r, echo=FALSE}
setwd("E:/LIBR/Data")
load("case.control_stat.RData")
load("self_reports_scores.RData")
load("narratives_notes.RData")
load("dep_measrd_scores.RData")

case.control_stat_M.A <- case.control_stat[which(case.control_stat$GroupAssignment=="Mood/Anxiety"), ]
SelfReport_M.A <- self_reports_scores[which(case.control_stat$GroupAssignment=="Mood/Anxiety"), ]
nrow(SelfReport_M.A)
narratives_notes_M.A <- narratives_notes[which(narratives_notes$id%in%SelfReport_M.A$id), ]
MeasrdScore_M.A <- dep_measrd_scores[which(dep_measrd_scores$id%in%SelfReport_M.A$id), ]

```

We start with an example: consider the following a random subject narrative note. 

```{r, echo=FALSE}
rand_subject <- 7
cat("A random narrative note:\n\n" ,as.character(narratives_notes_M.A[rand_subject, 2])) 
```

The following adjective words are selected from the above narrative note with an aggregated subjectivity score, subjectivity score normalized with all adjective words in this narrative note and subjectivity score nomalized with total words in this narrative note.

```{r, echo=FALSE}
temp_M.A <- MeasrdScore_M.A[rand_subject, ]
cat("Subjectivity Score:", temp_M.A$sub_score, "\nSubjectivity score-normalized by total adjective words:", temp_M.A$sub_score_norm, "\n\nSubjectivity score-normalized by total words:", temp_M.A$sub_score_totalNorm,"\n\nAdjective Words and their score:", as.character(temp_M.A$sub_words))
```

The following words with positive valence are selected from the above narrative note with an aggregated positive score, positive score normalized with all positive valence words in this narrative note and positive score normalized with total words in this narrative note.

```{r, echo=FALSE}
cat("Positive Score:", temp_M.A$pos_score, "\nPositive score-normalized by total adjective words", temp_M.A$pos_score_norm, "Positive score-normalized by total words:", temp_M.A$pos_score_totalNorm,"\n\nWords with positive valence and their score:", as.character(temp_M.A$pos_words))
```

The following words with negative valence are selected from the above narrative note with an aggregated negative score, negative score normalized with all negative valence words in this narrative note and negative score normalized with total words in this narrative note.

```{r, echo=FALSE}
cat("Negative Score:", temp_M.A$neg_score, "\nNegative score-normalized by total adjective words:", temp_M.A$neg_score_norm, "Negative score-normalized by total words:", temp_M.A$neg_score_totalNorm,"\n\nWords with negative valence and their score:", as.character(temp_M.A$neg_words))
```

In following histogram plots show the frequency of total number of words and adjective words:

```{r, echo=FALSE}
hist(MeasrdScore_M.A$total_words, col = "blue", main = "Histogram of total number of words",
     xlab = "Number of words")
hist(MeasrdScore_M.A$X..sub_words, col = "blue", main = "Histogram of total number of adjective words",
     xlab = "Number of words")
```

As we saw in above example, scores are nomalized by total words and total adjective words, and we are interested to choose those scores that more negatively correlated in positive scores and negative scores. Below, we check the correlation of three different types of dependend measure scores:

```{r, echo=FALSE}
library(psych)
# sum of score
Sub.score <- MeasrdScore_M.A$sub_score
Pos.score <- MeasrdScore_M.A$pos_score
Neg.score <- MeasrdScore_M.A$neg_score
pairs.panels(data.frame(Pos.score, Neg.score, Sub.score), main = "regular score")
# average scores
Sub.score.norm <- MeasrdScore_M.A$sub_score_norm
Pos.score.norm <- MeasrdScore_M.A$pos_score_norm
Neg.score.norm <- MeasrdScore_M.A$neg_score_norm
pairs.panels(data.frame(Pos.score.norm, Neg.score.norm, Sub.score.norm), main = "adjusted by valence words")
# average scores (Adjusted by total words)
Sub.score.tnorm <- MeasrdScore_M.A$sub_score_totalNorm
Pos.score.tnorm <- MeasrdScore_M.A$pos_score_totalNorm
Neg.score.tnorm <- MeasrdScore_M.A$neg_score_totalNorm
pairs.panels(data.frame(Pos.score.tnorm, Neg.score.tnorm, Sub.score.tnorm), main = "adjusted by total words")
```

It looks like that the regular scores without normalization is better choice. Thus, we compute the regular scores for all subjects independently. The following plots show the histogram of three different scores:

```{r fig.width=10, fig.height=3, echo=FALSE}
par(mfrow = c(1, 3))
# subjectivity score
hist(MeasrdScore_M.A$sub_score, main= "Histogram of Subjectivity Scores",xlab="Subjectivity Scores", ylim = c(0, 100))
# positive score
hist(MeasrdScore_M.A$pos_score, main = "Histogram of Positive Scores" ,xlab="Positive Score", ylim = c(0, 60))
# negative score
hist(MeasrdScore_M.A$neg_score, main= "Histogram of Negative Scores",xlab = "Negative Score", ylim = c(0, 80))
```

Association of total number of words and adjective words with PHQ, OASIS, AND CTQ

```{r, echo=FALSE}
total_words_M.A <- MeasrdScore_M.A$total_words
adj_words_M.A <- MeasrdScore_M.A$X..sub_words
pos_words_M.A <- MeasrdScore_M.A$X..pos.words
neg_words_M.A <- MeasrdScore_M.A$X..neg.words
PHQ_M.A <- SelfReport_M.A$PHQ
OASIS_M.A <- SelfReport_M.A$OASIS
CTQ_M.A <- SelfReport_M.A$CTQ_score

par(mfrow = c(2, 3))
lm.fit_PHQ <- lm(total_words_M.A ~ PHQ_M.A)
plot(PHQ_M.A, total_words_M.A, main = "effect of PHQ", xlab = "PHQ", ylab = "Total words")
abline(lm.fit_PHQ, col = "red")
PHQ_pval <- summary(lm.fit_PHQ)$coefficients[2,4]
legend(-3, 2000, legend = c("p-value", round(PHQ_pval, digits = 4)), cex = .9, bty = "n")

lm.fit_OASIS <- lm(total_words_M.A ~ OASIS_M.A)
plot(OASIS_M.A, total_words_M.A, main = "effect of OASIS", xlab = "OASIS", ylab = "Total words")
abline(lm.fit_OASIS, col = "red")
OASIS_pval <- summary(lm.fit_OASIS)$coefficients[2,4]
legend(-1, 2000, legend = c("p-value", round(OASIS_pval, digits = 4)), cex = .9, bty = "n")

lm.fit_CTQ <- lm(total_words_M.A ~ CTQ_M.A)
plot(CTQ_M.A, total_words_M.A, main = "effect of CTQ", xlab = "CTQ", ylab = "Total words")
abline(lm.fit_CTQ, col = "red")
CTQ_pval <- summary(lm.fit_CTQ)$coefficients[2,4]
legend(15, 2000, legend = c("p-value", round(CTQ_pval, digits = 4)), cex = .9, bty = "n")

lm.fit_PHQ <- lm(adj_words_M.A ~ PHQ_M.A)
plot(PHQ_M.A, adj_words_M.A, main = "effect of PHQ", xlab = "PHQ", ylab = "Adjective words")
abline(lm.fit_PHQ, col = "red")
PHQ_pval <- summary(lm.fit_PHQ)$coefficients[2,4]
legend(-3, 85, legend = c("p-value", round(PHQ_pval, digits = 4)), cex = .9, bty = "n")

lm.fit_OASIS <- lm(adj_words_M.A ~ OASIS_M.A)
plot(OASIS_M.A, adj_words_M.A, main = "effect of OASIS", xlab = "OASIS", ylab = "Adjective words")
abline(lm.fit_OASIS, col = "red")
OASIS_pval <- summary(lm.fit_OASIS)$coefficients[2,4]
legend(-1, 85, legend = c("p-value", round(OASIS_pval, digits = 4)), cex = .9, bty = "n")

lm.fit_CTQ <- lm(adj_words_M.A ~ CTQ_M.A)
plot(CTQ_M.A, adj_words_M.A, main = "effect of CTQ", xlab = "CTQ", ylab = "Adjective words")
abline(lm.fit_CTQ, col = "red")
CTQ_pval <- summary(lm.fit_CTQ)$coefficients[2,4]
legend(15, 85, legend = c("p-value", round(CTQ_pval, digits = 4)), cex = .9, bty = "n")
```


Extract Age, Gender, Income, and Education

```{r, echo=FALSE}
Age_M.A    <- case.control_stat_M.A[, grep("Age", names(SelfReport_M.A), fixed = T)]
Gender_M.A <- as.numeric(case.control_stat_M.A[, grep("Gender", names(SelfReport_M.A), fixed = T)])
Edu_M.A    <- case.control_stat_M.A[, grep("Education", names(SelfReport_M.A), fixed = T)]
Income_M.A <- log2(case.control_stat_M.A[, grep("Income", names(SelfReport_M.A), fixed = T)])
Income_M.A <- replace(Income_M.A, which(Income_M.A=="-Inf"), NA)
```

Determine the degree to which socio-demographic characteristics effect the dependent measures

```{r fig.width=10, fig.height=7, echo=FALSE}
# Subjectivity score as dependent measure
par(mfrow = c(3, 4))
lm.fit_age <- lm(Sub.score ~ Age_M.A)
age_pval <- summary(lm.fit_age)$coefficients[2,4]
plot(Age_M.A, Sub.score, main = "effect of age", xlab = c("p-value" ,round(age_pval, digits = 4)), ylab = "Subjectivity score")
abline(lm.fit_age, col = "red")

lm.fit_gender <- lm(Sub.score ~ Gender_M.A)
gender_pval <- summary(lm.fit_gender)$coefficients[2,4]
plot(Gender_M.A, Sub.score, main = "effect of gender", xlab = c("p-value" ,round(gender_pval, digits = 4)), ylab = "Subjectivity score")
abline(lm.fit_gender, col = "red")


lm.fit_edu <- lm(Sub.score ~ Edu_M.A)
edu_pval <- summary(lm.fit_edu)$coefficients[2,4]
plot(Edu_M.A, Sub.score, main = "effect of education", xlab = c("p-value" ,round(edu_pval, digits = 4)), ylab = "Subjectivity score")
abline(lm.fit_edu, col = "red")


lm.fit_inc <- lm(Sub.score ~ Income_M.A)
inc_pval <- summary(lm.fit_inc)$coefficients[2,4]
plot(Income_M.A, Sub.score, main = "effect of income", xlab = c("p-value" ,round(inc_pval, digits = 4)), ylab = "Subjectivity score")
abline(lm.fit_inc, col = "red")

# Positive score  as dependent measure
lm.fit_age <- lm(Pos.score ~ Age_M.A)
age_pval <- summary(lm.fit_age)$coefficients[2,4]
plot(Age_M.A, Pos.score, main = "effect of age", xlab = c("p-value" ,round(age_pval, digits = 4)), ylab = "positive score")
abline(lm.fit_age, col = "red")

lm.fit_gender <- lm(Pos.score ~ Gender_M.A)
gender_pval <- summary(lm.fit_gender)$coefficients[2,4]
plot(Gender_M.A, Pos.score, main = "effect of gender", xlab = c("p-value" ,round(gender_pval, digits = 4)), ylab = "positive score")
abline(lm.fit_gender, col = "red")

lm.fit_edu <- lm(Pos.score ~ Edu_M.A)
edu_pval <- summary(lm.fit_edu)$coefficients[2,4]
plot(Edu_M.A, Pos.score, main = "effect of education", xlab = c("p-value" ,round(edu_pval, digits = 4)), ylab = "positive score")
abline(lm.fit_edu, col = "red")

lm.fit_inc <- lm(Pos.score ~ Income_M.A)
inc_pval <- summary(lm.fit_inc)$coefficients[2,4]
plot(Income_M.A, Pos.score, main = "effect of income", xlab = c("p-value" ,round(inc_pval, digits = 4)), ylab = "positive score")
abline(lm.fit_inc, col = "red")

# Negative score  as dependent measure
lm.fit_age <- lm(Neg.score ~ Age_M.A)
age_pval <- summary(lm.fit_age)$coefficients[2,4]
plot(Age_M.A, Neg.score, main = "effect of age", xlab = c("p-value" ,round(age_pval, digits = 4)), ylab = "negative score")
abline(lm.fit_age, col = "red")

lm.fit_gender <- lm(Neg.score ~ Gender_M.A)
gender_pval <- summary(lm.fit_gender)$coefficients[2,4]
plot(Gender_M.A, Neg.score, main = "effect of gender ", xlab = c("p-value" ,round(gender_pval, digits = 4)), ylab = "negative score")
abline(lm.fit_gender, col = "red")

lm.fit_edu <- lm(Neg.score ~ Edu_M.A)
edu_pval <- summary(lm.fit_edu)$coefficients[2,4]
plot(Edu_M.A, Neg.score, main = "effect of education", xlab = c("p-value" ,round(edu_pval, digits = 4)), ylab = "negative score")
abline(lm.fit_edu, col = "red")

lm.fit_inc <- lm(Neg.score ~ Income_M.A)
inc_pval <- summary(lm.fit_inc)$coefficients[2,4]
plot(Income_M.A, Neg.score, main = "effect of income", xlab = c("p-value" ,round(inc_pval, digits = 4)), ylab = "negative score")
abline(lm.fit_inc, col = "red")
```

Determine the relationship with respect to the following trait variables:
(PANAS-X, BIF, Symptom scales PHQ-9) 

```{r fig.width=8, fig.height=7, echo=FALSE}
PANASX_pos_M.A <- SelfReport_M.A[ ,grepl("PANASX_PosAffect", names(SelfReport_M.A))]
PANASX_neg_M.A <- SelfReport_M.A[ ,grepl("PANASX_NegAffect", names(SelfReport_M.A))]
PHQ_M.A <- narratives_notes_M.A$PHQ

# Subjectivity score as dependent measure
par(mfrow = c(3, 3))
lm_fit_PAN.pos <- lm(Sub.score ~ PANASX_pos_M.A)
PAN.pos_pval <- summary(lm_fit_PAN.pos)$coefficients[2,4]
plot(PANASX_pos_M.A, Sub.score, main = "effect of PANASX positive", xlab = c("p-value" ,round(PAN.pos_pval, digits = 4)), ylab = "Subjectivity score")
abline(lm_fit_PAN.pos, col = "red")

lm_fit_PAN.neg <- lm(Sub.score ~ PANASX_neg_M.A)
PAN.neg_pval <- summary(lm_fit_PAN.neg)$coefficients[2,4]
plot(PANASX_neg_M.A, Sub.score, main = "effect of PANASX negative", xlab = c("p-value" ,round(PAN.neg_pval, digits = 4)), ylab = "Subjectivity score")
abline(lm_fit_PAN.neg, col = "red")

lm_fit_PHQ <- lm(Sub.score ~ PHQ_M.A)
PHQ_pval <- summary(lm_fit_PHQ)$coefficients[2,4]
plot(PHQ_M.A, Sub.score, main = "effect of PHQ", xlab = c("p-value" ,round(PHQ_pval, digits = 4)), ylab = "Subjectivity score")
abline(lm_fit_PHQ, col = "red")

# Positive score as dependent measure
lm_fit_PAN.pos <- lm(Pos.score ~ PANASX_pos_M.A)
PAN.pos_pval <- summary(lm_fit_PAN.pos)$coefficients[2,4]
plot(PANASX_pos_M.A, Pos.score, main = "effect of PANASX positive", xlab = c("p-value" ,round(PAN.pos_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_PAN.pos, col = "red")

lm_fit_PAN.neg <- lm(Pos.score ~ PANASX_neg_M.A)
PAN.neg_pval <- summary(lm_fit_PAN.neg)$coefficients[2,4]
plot(PANASX_neg_M.A, Pos.score, main = "effect of PANASX negative", xlab = c("p-value" ,round(PAN.neg_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_PAN.neg, col = "red")

lm_fit_PHQ <- lm(Pos.score ~ PHQ_M.A)
PHQ_pval <- summary(lm_fit_PHQ)$coefficients[2,4]
plot(PHQ_M.A, Pos.score, main = "effect of PHQ", xlab = c("p-value" ,round(PHQ_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_PHQ, col = "red")

# Negative score as dependent measure
lm_fit_PAN.pos <- lm(Neg.score ~ PANASX_pos_M.A)
PAN.pos_pval <- summary(lm_fit_PAN.pos)$coefficients[2,4]
plot(PANASX_pos_M.A, Neg.score, main = "effect of PANASX positive", xlab = c("p-value" ,round(PAN.pos_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_PAN.pos, col = "red")

lm_fit_PAN.neg <- lm(Neg.score ~ PANASX_neg_M.A)
PAN.neg_pval <- summary(lm_fit_PAN.neg)$coefficients[2,4]
plot(PANASX_neg_M.A, Neg.score, main = "effect of PANASX negative", xlab = c("p-value" ,round(PAN.neg_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_PAN.neg, col = "red")

lm_fit_PHQ <- lm(Neg.score ~ PHQ_M.A)
PHQ_pval <- summary(lm_fit_PHQ)$coefficients[2,4]
plot(PHQ_M.A, Neg.score, main = "effect of PHQ", xlab = c("p-value" ,round(PHQ_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_PHQ, col = "red")
```

```{r fig.width=10, fig.height=7, echo=FALSE}
BFI_con_M.A <- SelfReport_M.A[ ,grepl("BFI_Conscious", names(SelfReport_M.A))]
BFI_open_M.A <- SelfReport_M.A[ ,grepl("BFI_Openness", names(SelfReport_M.A))]
BFI_agree_M.A <- SelfReport_M.A[ ,grepl("BFI_Agreeb", names(SelfReport_M.A))]
BFI_extrav_M.A <- SelfReport_M.A[ ,grepl("BFI_Extrav", names(SelfReport_M.A))]
BFI_neurot_M.A <- SelfReport_M.A[ ,grepl("BFI_Neurot", names(SelfReport_M.A))]

# Subjectivity score as dependent measure
par(mfrow = c(3, 5))
lm_fit_BFI.con <- lm(Sub.score ~ BFI_con_M.A)
BFI.con_pval <- summary(lm_fit_BFI.con)$coefficients[2,4]
plot(BFI_con_M.A, Sub.score, main = "effect of BFI conscious", xlab = c("p-value" ,round(BFI.con_pval, digits = 4)), ylab = "Subjectivity score")
abline(lm_fit_BFI.con, col = "red")

lm_fit_BFI.open <- lm(Sub.score ~ BFI_open_M.A)
BFI.open_pval <- summary(lm_fit_BFI.open)$coefficients[2,4]
plot(BFI_open_M.A, Sub.score, main = "effect of BFI openness", xlab = c("p-value" ,round(BFI.open_pval, digits = 4)), ylab = "Subjectivity score")
abline(lm_fit_BFI.open, col = "red")

lm_fit_BFI.agree <- lm(Sub.score ~ BFI_agree_M.A)
BFI.agree_pval <- summary(lm_fit_BFI.agree)$coefficients[2,4]
plot(BFI_agree_M.A, Sub.score, main = "effect of BFI Agreeb", xlab = c("p-value" ,round(BFI.agree_pval, digits = 4)), ylab = "Subjectivity score")
abline(lm_fit_BFI.agree, col = "red")

lm_fit_BFI.extrav <- lm(Sub.score ~ BFI_extrav_M.A)
BFI.extrav_pval <- summary(lm_fit_BFI.extrav)$coefficients[2,4]
plot(BFI_extrav_M.A, Sub.score, main = "effect of BFI Extrav", xlab = c("p-value" ,round(BFI.extrav_pval, digits = 4)), ylab = "Subjectivity score")
abline(lm_fit_BFI.extrav, col = "red")

lm_fit_BFI.neurot <- lm(Sub.score ~ BFI_neurot_M.A)
BFI.neurot_pval <- summary(lm_fit_BFI.neurot)$coefficients[2,4]
plot(BFI_neurot_M.A, Sub.score, main = "effect of BFI Neurot", xlab = c("p-value" ,round(BFI.neurot_pval, digits = 4)), ylab = "Subjectivity score")
abline(lm_fit_BFI.neurot, col = "red")

# Positive score as dependent measure
lm_fit_BFI.con <- lm(Pos.score ~ BFI_con_M.A)
BFI.con_pval <- summary(lm_fit_BFI.con)$coefficients[2,4]
plot(BFI_con_M.A, Pos.score, main = "effect of BFI conscious", xlab = c("p-value" ,round(BFI.con_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_BFI.con, col = "red")

lm_fit_BFI.open <- lm(Pos.score ~ BFI_open_M.A)
BFI.open_pval <- summary(lm_fit_BFI.open)$coefficients[2,4]
plot(BFI_open_M.A, Pos.score, main = "effect of BFI openness", xlab = c("p-value" ,round(BFI.open_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_BFI.open, col = "red")

lm_fit_BFI.agree <- lm(Pos.score ~ BFI_agree_M.A)
BFI.agree_pval <- summary(lm_fit_BFI.agree)$coefficients[2,4]
plot(BFI_agree_M.A, Pos.score, main = "effect of BFI Agreeb", xlab = c("p-value" ,round(BFI.agree_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_BFI.agree, col = "red")

lm_fit_BFI.extrav <- lm(Pos.score ~ BFI_extrav_M.A)
BFI.extrav_pval <- summary(lm_fit_BFI.extrav)$coefficients[2,4]
plot(BFI_extrav_M.A, Pos.score, main = "effect of BFI Extrav", xlab = c("p-value" ,round(BFI.extrav_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_BFI.extrav, col = "red")

lm_fit_BFI.neurot <- lm(Pos.score ~ BFI_neurot_M.A)
BFI.neurot_pval <- summary(lm_fit_BFI.neurot)$coefficients[2,4]
plot(BFI_neurot_M.A, Pos.score, main = "effect of BFI Neurot", xlab = c("p-value" ,round(BFI.neurot_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_BFI.neurot, col = "red")

# Negative score as dependent measure
lm_fit_BFI.con <- lm(Neg.score ~ BFI_con_M.A)
BFI.con_pval <- summary(lm_fit_BFI.con)$coefficients[2,4]
plot(BFI_con_M.A, Neg.score, main = "effect of BFI conscious", xlab = c("p-value" ,round(BFI.con_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_BFI.con, col = "red")

lm_fit_BFI.open <- lm(Neg.score ~ BFI_open_M.A)
BFI.open_pval <- summary(lm_fit_BFI.open)$coefficients[2,4]
plot(BFI_open_M.A, Neg.score, main = "effect of BFI openness", xlab = c("p-value" ,round(BFI.open_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_BFI.open, col = "red")

lm_fit_BFI.agree <- lm(Neg.score ~ BFI_agree_M.A)
BFI.agree_pval <- summary(lm_fit_BFI.agree)$coefficients[2,4]
plot(BFI_agree_M.A, Neg.score, main = "effect of BFI Agreeb", xlab = c("p-value" ,round(BFI.agree_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_BFI.agree, col = "red")

lm_fit_BFI.extrav <- lm(Neg.score ~ BFI_extrav_M.A)
BFI.extrav_pval <- summary(lm_fit_BFI.extrav)$coefficients[2,4]
plot(BFI_extrav_M.A, Neg.score, main = "effect of BFI Extrav", xlab = c("p-value" ,round(BFI.extrav_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_BFI.extrav, col = "red")

lm_fit_BFI.neurot <- lm(Neg.score ~ BFI_neurot_M.A)
BFI.neurot_pval <- summary(lm_fit_BFI.neurot)$coefficients[2,4]
plot(BFI_neurot_M.A, Neg.score, main = "effect of BFI Neurot", xlab = c("p-value" ,round(BFI.neurot_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_BFI.neurot, col = "red")
```

Determine the relationship with respect to the following trait variables:
(Symptom scales OASIS), PROMIS (anxiety, depression, anger), Interviewers)

```{r fig.width=10, fig.height=7, echo=FALSE}
OASIS_M.A <- case.control_stat_M.A$OASIS
PROMIS.Ang_M.A <- SelfReport_M.A[ ,grepl("PROMIS_AngerTscore", names(SelfReport_M.A))]
PROMIS.Dep_M.A <- SelfReport_M.A[ , grepl("PROMIS_DepressTscore", names(SelfReport_M.A))]
PROMIS.Anx_M.A <- SelfReport_M.A[ , grepl("PROMIS_AnxietyTscore", names(SelfReport_M.A))]
LC_M.A <- as.numeric(narratives_notes_M.A$LC_conducted_by)

# Subjectivity score as dependent measure
par(mfrow = c(3, 5))
lm_fit_OASIS <- lm(Sub.score ~ OASIS_M.A)
OASIS_pval <- summary(lm_fit_OASIS)$coefficients[2,4]
plot(OASIS_M.A, Sub.score, main = "effect of OASIS", xlab =c("p-value" ,round(OASIS_pval, digits = 4)), ylab = "Subjectivity score")
abline(lm_fit_OASIS, col = "red")

lm_fit_PROMIS.Ang <- lm(Sub.score ~ PROMIS.Ang_M.A)
PROMIS.Ang_pval <- summary(lm_fit_PROMIS.Ang)$coefficients[2,4]
plot(PROMIS.Ang_M.A, Sub.score, main = "effect of PROMIS Anger", xlab = c("p-value" ,round(PROMIS.Ang_pval, digits = 4)), ylab = "Subjectivity score")
abline(lm_fit_PROMIS.Ang, col = "red")

lm_fit_PROMIS.Dep <- lm(Sub.score ~ PROMIS.Dep_M.A)
PROMIS.Dep_pval <- summary(lm_fit_PROMIS.Dep)$coefficients[2,4]
plot(PROMIS.Dep_M.A, Sub.score, main = "effect of PROMIS Depress", xlab = c("p-value" ,round(PROMIS.Dep_pval, digits = 4)), ylab = "Subjectivity score")
abline(lm_fit_PROMIS.Dep, col = "red")

lm_fit_PROMIS.Anx <- lm(Sub.score ~ PROMIS.Anx_M.A)
PROMIS.Anx_pval <- summary(lm_fit_PROMIS.Anx)$coefficients[2,4]
plot(PROMIS.Anx_M.A, Sub.score, main = "effect of PROMIS Anxiety", xlab =c("p-value" ,round(PROMIS.Anx_pval, digits = 4)), ylab = "Subjectivity score")
abline(lm_fit_PROMIS.Anx, col = "red")

lm_fit_LC <- lm(Sub.score ~ LC_M.A)
LC_pval <- summary(lm_fit_LC)$coefficients[2,4]
sub_LC <- data.frame(Sub.score,LC_M.A)
boxplot(Sub.score~LC_M.A, data= sub_LC,main = "effect of LC", xlab = c("p-value" ,round(LC_pval, digits = 4)), ylab = "Subjectivity score")
abline(lm_fit_LC, col = "red")

# Positive score as dependent measure
lm_fit_OASIS <- lm(Pos.score ~ OASIS_M.A)
OASIS_pval <- summary(lm_fit_OASIS)$coefficients[2,4]
plot(OASIS_M.A, Pos.score, main = "effect of OASIS", xlab = c("p-value" ,round(OASIS_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_OASIS, col = "red")

lm_fit_PROMIS.Ang <- lm(Pos.score ~ PROMIS.Ang_M.A)
PROMIS.Ang_pval <- summary(lm_fit_PROMIS.Ang)$coefficients[2,4]
plot(PROMIS.Ang_M.A, Pos.score, main = "effect of PROMIS Anger", xlab = c("p-value" ,round(PROMIS.Ang_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_PROMIS.Ang, col = "red")

lm_fit_PROMIS.Dep <- lm(Pos.score ~ PROMIS.Dep_M.A)
PROMIS.Dep_pval <- summary(lm_fit_PROMIS.Dep)$coefficients[2,4]
plot(PROMIS.Dep_M.A, Pos.score, main = "effect of PROMIS Depress", xlab = c("p-value" ,round(PROMIS.Dep_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_PROMIS.Dep, col = "red")

lm_fit_PROMIS.Anx <- lm(Pos.score ~ PROMIS.Anx_M.A)
PROMIS.Anx_pval <- summary(lm_fit_PROMIS.Anx)$coefficients[2,4]
plot(PROMIS.Anx_M.A, Pos.score, main = "effect of PROMIS Anxiety", xlab = c("p-value" ,round(PROMIS.Anx_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_PROMIS.Anx, col = "red")

lm_fit_LC <- lm(Pos.score ~ LC_M.A)
LC_pval <- summary(lm_fit_LC)$coefficients[2,4]
pos_LC <- data.frame(Pos.score, LC_M.A)
boxplot(Pos.score~LC_M.A, data= pos_LC, main = "effect of LC", xlab = c("p-value" ,round(LC_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_LC, col = "red")

# Negative score as dependent measure
lm_fit_OASIS <- lm(Neg.score ~ OASIS_M.A)
OASIS_pval <- summary(lm_fit_OASIS)$coefficients[2,4]
plot(OASIS_M.A, Neg.score, main = "effect of OASIS", xlab = c("p-value" ,round(OASIS_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_OASIS, col = "red")

lm_fit_PROMIS.Ang <- lm(Neg.score ~ PROMIS.Ang_M.A)
PROMIS.Ang_pval <- summary(lm_fit_PROMIS.Ang)$coefficients[2,4]
plot(PROMIS.Ang_M.A, Neg.score, main = "effect of PROMIS Anger", xlab =c("p-value" ,round(PROMIS.Ang_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_PROMIS.Ang, col = "red")

lm_fit_PROMIS.Dep <- lm(Neg.score ~ PROMIS.Dep_M.A)
PROMIS.Dep_pval <- summary(lm_fit_PROMIS.Dep)$coefficients[2,4]
plot(PROMIS.Dep_M.A, Neg.score, main = "effect of PROMIS Depress", xlab = c("p-value" ,round(PROMIS.Dep_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_PROMIS.Dep, col = "red")

lm_fit_PROMIS.Anx <- lm(Neg.score ~ PROMIS.Anx_M.A)
PROMIS.Anx_pval <- summary(lm_fit_PROMIS.Anx)$coefficients[2,4]
plot(PROMIS.Anx_M.A, Neg.score, main = "effect of PROMIS Anxiety", xlab = c("p-value" ,round(PROMIS.Anx_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_PROMIS.Anx, col = "red")

lm_fit_LC <- lm(Neg.score ~ LC_M.A)
neg_LC <- data.frame(Neg.score, LC_M.A)
boxplot(Neg.score~LC_M.A, data= neg_LC, main = "effect of LC", xlab = c("p-value" ,round(LC_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_LC, col = "red")
```

Determine mediating influences (CTQ, TEC)on dependent measured scores

```{r fig.width=8, fig.height=7, echo=FALSE}
CTQ_M.A <- SelfReport_M.A[ ,grepl("CTQ_score", names(SelfReport_M.A))]
TES_M.A <- SelfReport_M.A[ ,grepl("TES_TotalOccurrence", names(SelfReport_M.A))]
DAST_M.A <- case.control_stat_M.A[ ,grepl("DAST", names(SelfReport_M.A))]

# mood and anxiety
# Subjectivity score as dependent measure
par(mfrow = c(3, 3))
lm_fit_CTQ <- lm(Sub.score ~ CTQ_M.A)
CTQ_pval <- summary(lm_fit_CTQ)$coefficients[2,4]
plot(CTQ_M.A, Sub.score, main = "effect of CTQ (mood/anxiety)", xlab = c("p-value" ,round(CTQ_pval, digits = 4)), ylab = "Subjectivity score")
abline(lm_fit_CTQ, col = "red")

lm_fit_TES <- lm(Sub.score ~ TES_M.A)
TES_pval <- summary(lm_fit_TES)$coefficients[2,4]
plot(TES_M.A, Sub.score, main = "effect of TES (mood/anxiety)", xlab = c("p-value" ,round(TES_pval, digits = 4)), ylab = "Subjectivity score")
abline(lm_fit_TES, col = "red")

lm_fit_DAST <- lm(Sub.score ~ DAST_M.A)
DAST_pval <- summary(lm_fit_DAST)$coefficients[2,4]
plot(DAST_M.A, Sub.score, main = "effect of DAST (mood/anxiety)", xlab = c("p-value" ,round(DAST_pval, digits = 4)), ylab = "Subjectivity score")
abline(lm_fit_DAST, col = "red")

# Positive score as dependent measure
lm_fit_CTQ <- lm(Pos.score ~ CTQ_M.A)
CTQ_pval <- summary(lm_fit_CTQ)$coefficients[2,4]
plot(CTQ_M.A, Pos.score, main = "effect of CTQ (mood/anxiety)", xlab =c("p-value" ,round(CTQ_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_CTQ, col = "red")

lm_fit_TES <- lm(Pos.score ~ TES_M.A)
TES_pval <- summary(lm_fit_TES)$coefficients[2,4]
plot(TES_M.A, Pos.score, main = "effect of TES (mood/anxiety)", xlab = c("p-value" ,round(TES_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_TES, col = "red")

lm_fit_DAST <- lm(Pos.score ~ DAST_M.A)
DAST_pval <- summary(lm_fit_DAST)$coefficients[2,4]
plot(DAST_M.A, Pos.score, main = "effect of DAST (mood/anxiety)", xlab = c("p-value" ,round(DAST_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_DAST, col = "red")

# Negative score as dependent measure
lm_fit_CTQ <- lm(Neg.score ~ CTQ_M.A)
CTQ_pval <- summary(lm_fit_CTQ)$coefficients[2,4]
plot(CTQ_M.A, Neg.score, main = "effect of CTQ (mood/anxiety)", xlab = c("p-value" ,round(CTQ_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_CTQ, col = "red")

lm_fit_TES <- lm(Neg.score ~ TES_M.A)
TES_pval <- summary(lm_fit_TES)$coefficients[2,4]
plot(TES_M.A, Neg.score, main = "effect of TES (mood/anxiety)", xlab = c("p-value" ,round(TES_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_TES, col = "red")

lm_fit_DAST <- lm(Neg.score ~ DAST_M.A)
DAST_pval <- summary(lm_fit_DAST)$coefficients[2,4]
plot(DAST_M.A, Neg.score, main = "effect of DAST (mood/anxiety)", xlab = c("p-value" ,round(DAST_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_DAST, col = "red")
```

Severity of disorders between interviewers (PHQ, OASIS) if patients' score is the same, are the notes in the same lenghth as well?

```{r, echo=FALSE}
Severity_df <- cbind.data.frame(OASIS = OASIS_M.A, PHQ = PHQ_M.A, Total_words = total_words_M.A, Interviewer = as.character(narratives_notes_M.A$LC_conducted_by))

# Severity sorted by PHQ
Severity_sort.1 <- Severity_df[order(Severity_df[,2], decreasing = TRUE),]
# patients with same PHQ
head(Severity_sort.1, 15)

# Severity sorted by OASIS
Severity_sort.2 <- Severity_df[order(Severity_df[,1], decreasing = TRUE ),]
# patients with same OASIS
head(Severity_sort.2, 15)

# common OASIS and PHQ
Severity_df[which(Severity_df[,1]==Severity_df[,2]), ]
```

Concatenate all the valence words, and find the frequency of each word

```{r, echo=FALSE}
# concatenate valence words
pos_words <- gsub("[[:punct:]]", "", MeasrdScore_M.A$pos_words)
pos_words <- gsub('[0-9]+', '', pos_words)
neg_words <- gsub("[[:punct:]]", "", MeasrdScore_M.A$neg_words)
neg_words <- gsub('[0-9]+', '', neg_words)
sub_words <- gsub("[[:punct:]]", "", dep_measrd_scores$sub_words)
sub_words <- gsub('[0-9]+', '', sub_words) 
valence_words <- c(tolower(pos_words), tolower(neg_words), tolower(sub_words))
valence_words <- paste(valence_words, collapse = '')
valence_words <- strsplit(valence_words, " ")
# Top 200 words with highest frequency
head(sort(table(valence_words), decreasing = TRUE), 100)
```