---
title: "Association between sentiment scores and T-500 self-reported scores in Mood/Anxiety group"
author: "Saeid Parvandeh"
date: "October 2017"
output: html_document
---
Analysis description:
T-500 self-reported data base consists of various coded claim data associated with each subject with which it captures only some elements from clinical representation. We motivated to use Natural Language Processing methods to measure other benefits from narrative discharge summaries--lifechart narrative note that is a short story of subject's life. Using Natural Language Toolkit (NLTK) library, we analyzed each narrative note to aggregated sentiment scores associated with each subject's lifechart. Thus, we found four sentiment scores based on valence words, positive score (0 to 1), negative score (-1 to 0), objectivity score(0 to 1, i.e. this is also known as objectivity score, a 0 score mean subjective and 1 means objective), and polarity score (-1 to +1). Here is the definition of each score, beriefly:

-The compound score is computed by summing the valence scores of each word in the lexicon, adjusted according to the rules, and then normalized to be between -1 (most extreme negative) and +1 (most extreme positive)

-The positive, objectivity, and negative scores are ratios for proportions of text that fall in each category.


In this report, we investigate the association of these four scores with self-reposted scores in T-500 data base for mood/anxitey group.

- Number of subjects in mood/axiety.

```{r, echo=FALSE}
setwd("E:/LIBR/new version/Data")
load("case.control_stat.RData")
load("self_reports_scores.RData")
load("narratives_notes.RData")
load("sentiment_scores.RData")

case.control_stat_MA <- case.control_stat[which(case.control_stat$GroupAssignment=="Mood/Anxiety"), ]
SelfReport_MA <- self_reports_scores[which(case.control_stat$GroupAssignment=="Mood/Anxiety"), ]
nrow(SelfReport_MA)
narratives_notes_MA <- narratives_notes[which(narratives_notes$id%in%SelfReport_MA$id), ]
MeasrdScore_MA <- sentiment_scores[which(sentiment_scores$id%in%SelfReport_MA$id), ]
```

- A simple example to show how the analysis work. The following sentences selected from T-500 narrative reports: 

```{r, echo=FALSE}
cat("####################################")
```
The subject was born in Boston and her family moved to Tulsa when she was 5 years old. She stated that she and her sister were teased constantly throughout elementary school because of their accents. She stated that she was overweight and would be called "hippo" by fellow students. She said that the teasing impacted her deeply and her self esteem suffered as a result. She stated that in order to fit in with her classmates, she began using marijuana and alcohol at 14 years old. She would smoke daily and drink occasionally at parties. She began acting out soon after her drug use began and started getting in trouble at school. She eventually ran away from home for 3 days due to the tension in the home between her and her mother. At 16 years old she got pregnant and was "forced to abort the baby" by her mother. She reports being given an ultimatum by her mother to either abort the child or be thrown out of the home and onto the street.

fit        (Polarity = 1.5, Intensity = 1.0247)

forced     (Polarity = -2.0, Intensity = 0.63246)

overweight (Polarity = -1.5, Intensity = 0.67082)

parties    (Polarity = 1.7, Intensity = 0.78102)

suffered  (Polarity = -2.2, Intensity = 0.74833) 

teased    (Polarity = -1.2, Intensity = 0.87178)

teasing   (Polarity = -0.3, Intensity = 1.1)

tension   (Polarity = -1.3, Intensity = 1.00499)

trouble   (Polarity = -1.7, Intensity = 0.64031)

- Three random sentences:

1. Grew up in New Jersey, one of 9 children.

Polarity: 0.0, 
Negative: 0.0, 
objectivity: 1.0, 
Positive: 0.0,

2. At 14 years old, the subject's mother attempted suicide and was hospitalized for several weeks.

Valence words: ("suicide", polarity: -3.5, intensity: 0.67082)

Polarity: -0.6705, 
Negative: 0.243, 
objectivity: 0.757, 
Positive: 0.0,


3. She reports currently being happy and functioning well.

Valence words: ("happy", polarity: 2.7, intensity: 0.9, "well", polarity: 1.1, intensity: 1.04403)

Polarity: 0.7003, 
Negative: 0.0, 
objectivity: 0.508, 
Positive: 0.492, 
```{r, echo=FALSE}
cat("####################################")
```

- Correlation between dependend scores:

```{r, echo=FALSE}
library(psych)
library(psych)
# sum of score
pos.score <- MeasrdScore_MA$pos
neg.score <- MeasrdScore_MA$neg
obj.score <- MeasrdScore_MA$obj
pol.score <- MeasrdScore_MA$pol
tot.words <- MeasrdScore_MA$total_words
tot.sen   <- MeasrdScore_MA$total_sen
pairs.panels(data.frame(pos.score, neg.score, obj.score, pol.score, tot.words, tot.sen), main = "regular score")
```

- Histogram of dependent scores:

```{r fig.width=10, fig.height=10, echo=FALSE}
par(mfrow=c(2, 2))
hist(MeasrdScore_MA$pos, col = "blue", main = "Histogram of positive scores",     xlab = "positive scores", breaks = 50, prob = T)
curve(dnorm(x, mean=mean(MeasrdScore_MA$pos), sd=sd(MeasrdScore_MA$pos)), add = TRUE)
hist(MeasrdScore_MA$neg, col = "blue", main = "Histogram of negative scores",     xlab = "negative scores", breaks = 50, prob = T)
curve(dnorm(x, mean=mean(MeasrdScore_MA$neg), sd=sd(MeasrdScore_MA$neg)), add = TRUE)
hist(MeasrdScore_MA$obj, col = "blue", main = "Histogram of objectivity scores",     xlab = "objectivity scores", breaks = 50, prob = T)
curve(dnorm(x, mean=mean(MeasrdScore_MA$obj), sd=sd(MeasrdScore_MA$obj)), add = TRUE)
hist(MeasrdScore_MA$pol, col = "blue", main = "Histogram of polarity scores",     xlab = "polarity scores", breaks = 50, prob = T)
curve(dnorm(x, mean=mean(MeasrdScore_MA$pol), sd=sd(MeasrdScore_MA$pol)), add = TRUE)
```



```{r, echo=FALSE}
Age_MA    <- case.control_stat_MA[, grep("Age", names(SelfReport_MA), fixed = T)]
Gender_MA <- as.numeric(case.control_stat_MA[, grep("Gender", names(SelfReport_MA), fixed = T)])
Edu_MA    <- case.control_stat_MA[, grep("Education", names(SelfReport_MA), fixed = T)]
Income_MA <- log2(case.control_stat_MA[, grep("Income", names(SelfReport_MA), fixed = T)])
Income_MA <- replace(Income_MA, which(Income_MA=="-Inf"), NA)
LC_MA <- as.numeric(narratives_notes_MA$LC_conducted_by)
```

- Interviewers effect on dependent scores:

```{r, echo=FALSE}
lc_ma_fit <- lm(LC_MA ~ tot.sen+tot.words+pos.score+neg.score+obj.score+pol.score)
anova(lc_ma_fit)[1:6, c(1, 5)]
```

- Determine the degree to which socio-demographic characteristics effect the dependent scores

```{r fig.width=8, fig.height=9, echo=FALSE}
par(mfrow = c(4, 4))
# Positive score as dependent measure
lm.fit_age <- lm(pos.score ~ Age_MA)
age_pval <- summary(lm.fit_age)$coefficients[2,4]
plot(Age_MA, pos.score, main = "age", xlab = c("p-value" ,round(age_pval, digits = 4)), ylab = "Positive score")
abline(lm.fit_age, col = "red")

lm.fit_gender <- lm(pos.score ~ Gender_MA)
gender_pval <- summary(lm.fit_gender)$coefficients[2,4]
plot(Gender_MA, pos.score, main = "gender", xlab = c("p-value" ,round(gender_pval, digits = 4)), ylab = "Positive score")
abline(lm.fit_gender, col = "red")


lm.fit_edu <- lm(pos.score ~ Edu_MA)
edu_pval <- summary(lm.fit_edu)$coefficients[2,4]
plot(Edu_MA, pos.score, main = "education", xlab = c("p-value" ,round(edu_pval, digits = 4)), ylab = "Positive score")
abline(lm.fit_edu, col = "red")


lm.fit_inc <- lm(pos.score ~ Income_MA)
inc_pval <- summary(lm.fit_inc)$coefficients[2,4]
plot(Income_MA, pos.score, main = "income", xlab = c("p-value" ,round(inc_pval, digits = 4)), ylab = "Positive score")
abline(lm.fit_inc, col = "red")

# Negetive score  as dependent measure
lm.fit_age <- lm(neg.score ~ Age_MA)
age_pval <- summary(lm.fit_age)$coefficients[2,4]
plot(Age_MA, neg.score, main = "age", xlab = c("p-value" ,round(age_pval, digits = 4)), ylab = "Negative score")
abline(lm.fit_age, col = "red")

lm.fit_gender <- lm(neg.score ~ Gender_MA)
gender_pval <- summary(lm.fit_gender)$coefficients[2,4]
plot(Gender_MA, neg.score, main = "gender", xlab = c("p-value" ,round(gender_pval, digits = 4)), ylab = "Negative score")
abline(lm.fit_gender, col = "red")

lm.fit_edu <- lm(neg.score ~ Edu_MA)
edu_pval <- summary(lm.fit_edu)$coefficients[2,4]
plot(Edu_MA, neg.score, main = "education", xlab = c("p-value" ,round(edu_pval, digits = 4)), ylab = "Negative score")
abline(lm.fit_edu, col = "red")

lm.fit_inc <- lm(neg.score ~ Income_MA)
inc_pval <- summary(lm.fit_inc)$coefficients[2,4]
plot(Income_MA, neg.score, main = "income", xlab = c("p-value" ,round(inc_pval, digits = 4)), ylab = "Negative score")
abline(lm.fit_inc, col = "red")

# objectivity score  as dependent measure
lm.fit_age <- lm(obj.score ~ Age_MA)
age_pval <- summary(lm.fit_age)$coefficients[2,4]
plot(Age_MA, obj.score, main = "age", xlab = c("p-value" ,round(age_pval, digits = 4)), ylab = "objectivity score")
abline(lm.fit_age, col = "red")

lm.fit_gender <- lm(obj.score ~ Gender_MA)
gender_pval <- summary(lm.fit_gender)$coefficients[2,4]
plot(Gender_MA, obj.score, main = "gender ", xlab = c("p-value" ,round(gender_pval, digits = 4)), ylab = "objectivity score")
abline(lm.fit_gender, col = "red")

lm.fit_edu <- lm(obj.score ~ Edu_MA)
edu_pval <- summary(lm.fit_edu)$coefficients[2,4]
plot(Edu_MA, obj.score, main = "education", xlab = c("p-value" ,round(edu_pval, digits = 4)), ylab = "objectivity score")
abline(lm.fit_edu, col = "red")

lm.fit_inc <- lm(obj.score ~ Income_MA)
inc_pval <- summary(lm.fit_inc)$coefficients[2,4]
plot(Income_MA, obj.score, main = "income", xlab = c("p-value" ,round(inc_pval, digits = 4)), ylab = "objectivity score")
abline(lm.fit_inc, col = "red")

# Polarity score  as dependent measure
lm.fit_age <- lm(pol.score ~ Age_MA)
age_pval <- summary(lm.fit_age)$coefficients[2,4]
plot(Age_MA, pol.score, main = "age", xlab = c("p-value" ,round(age_pval, digits = 4)), ylab = "Polarity score")
abline(lm.fit_age, col = "red")

lm.fit_gender <- lm(pol.score ~ Gender_MA)
gender_pval <- summary(lm.fit_gender)$coefficients[2,4]
plot(Gender_MA, pol.score, main = "gender ", xlab = c("p-value" ,round(gender_pval, digits = 4)), ylab = "Polarity score")
abline(lm.fit_gender, col = "red")

lm.fit_edu <- lm(pol.score ~ Edu_MA)
edu_pval <- summary(lm.fit_edu)$coefficients[2,4]
plot(Edu_MA, pol.score, main = "education", xlab = c("p-value" ,round(edu_pval, digits = 4)), ylab = "Polarity score")
abline(lm.fit_edu, col = "red")

lm.fit_inc <- lm(pol.score ~ Income_MA)
inc_pval <- summary(lm.fit_inc)$coefficients[2,4]
plot(Income_MA, pol.score, main = "income", xlab = c("p-value" ,round(inc_pval, digits = 4)), ylab = "Polarity score")
abline(lm.fit_inc, col = "red")
```

- Determine the relationship with respect to the following trait variables:
(PANAS-X, BIF, Symptom scales PHQ-9) 

```{r fig.width=8, fig.height=7, echo=FALSE}
PANASX_pos_MA <- SelfReport_MA[ ,grepl("PANASX_PosAffect", names(SelfReport_MA))]
PANASX_neg_MA <- SelfReport_MA[ ,grepl("PANASX_NegAffect", names(SelfReport_MA))]
PHQ_MA <- narratives_notes_MA$PHQ

# Positive score as dependent measure
par(mfcol = c(3, 4))
lm_fit_PAN.pos <- lm(pos.score ~ PANASX_pos_MA)
PAN.pos_pval <- summary(lm_fit_PAN.pos)$coefficients[2,4]
plot(PANASX_pos_MA, pos.score, main = "PANASX positive", xlab = c("p-value" ,round(PAN.pos_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_PAN.pos, col = "red")

lm_fit_PAN.neg <- lm(pos.score ~ PANASX_neg_MA)
PAN.neg_pval <- summary(lm_fit_PAN.neg)$coefficients[2,4]
plot(PANASX_neg_MA, pos.score, main = "PANASX negative", xlab = c("p-value" ,round(PAN.neg_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_PAN.neg, col = "red")

lm_fit_PHQ <- lm(pos.score ~ PHQ_MA)
PHQ_pval <- summary(lm_fit_PHQ)$coefficients[2,4]
plot(PHQ_MA, pos.score, main = "PHQ", xlab = c("p-value" ,round(PHQ_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_PHQ, col = "red")

# Negative score as dependent measure
lm_fit_PAN.pos <- lm(neg.score ~ PANASX_pos_MA)
PAN.pos_pval <- summary(lm_fit_PAN.pos)$coefficients[2,4]
plot(PANASX_pos_MA, neg.score, main = "PANASX positive", xlab = c("p-value" ,round(PAN.pos_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_PAN.pos, col = "red")

lm_fit_PAN.neg <- lm(neg.score ~ PANASX_neg_MA)
PAN.neg_pval <- summary(lm_fit_PAN.neg)$coefficients[2,4]
plot(PANASX_neg_MA, neg.score, main = "PANASX negative", xlab = c("p-value" ,round(PAN.neg_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_PAN.neg, col = "red")

lm_fit_PHQ <- lm(neg.score ~ PHQ_MA)
PHQ_pval <- summary(lm_fit_PHQ)$coefficients[2,4]
plot(PHQ_MA, neg.score, main = "PHQ", xlab = c("p-value" ,round(PHQ_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_PHQ, col = "red")

# objectivity score as dependent measure
lm_fit_PAN.pos <- lm(obj.score ~ PANASX_pos_MA)
PAN.pos_pval <- summary(lm_fit_PAN.pos)$coefficients[2,4]
plot(PANASX_pos_MA, obj.score, main = "PANASX positive", xlab = c("p-value" ,round(PAN.pos_pval, digits = 4)), ylab = "objectivity score")
abline(lm_fit_PAN.pos, col = "red")

lm_fit_PAN.neg <- lm(obj.score ~ PANASX_neg_MA)
PAN.neg_pval <- summary(lm_fit_PAN.neg)$coefficients[2,4]
plot(PANASX_neg_MA, obj.score, main = "PANASX negative", xlab = c("p-value" ,round(PAN.neg_pval, digits = 4)), ylab = "objectivity score")
abline(lm_fit_PAN.neg, col = "red")

lm_fit_PHQ <- lm(obj.score ~ PHQ_MA)
PHQ_pval <- summary(lm_fit_PHQ)$coefficients[2,4]
plot(PHQ_MA, obj.score, main = "PHQ", xlab = c("p-value" ,round(PHQ_pval, digits = 4)), ylab = "objectivity score")
abline(lm_fit_PHQ, col = "red")

# Polarity score as dependent measure
lm_fit_PAN.pos <- lm(pol.score ~ PANASX_pos_MA)
PAN.pos_pval <- summary(lm_fit_PAN.pos)$coefficients[2,4]
plot(PANASX_pos_MA, pol.score, main = "PANASX positive", xlab = c("p-value" ,round(PAN.pos_pval, digits = 4)), ylab = "Polarity score")
abline(lm_fit_PAN.pos, col = "red")

lm_fit_PAN.neg <- lm(pol.score ~ PANASX_neg_MA)
PAN.neg_pval <- summary(lm_fit_PAN.neg)$coefficients[2,4]
plot(PANASX_neg_MA, pol.score, main = "PANASX negative", xlab = c("p-value" ,round(PAN.neg_pval, digits = 4)), ylab = "Polarity score")
abline(lm_fit_PAN.neg, col = "red")

lm_fit_PHQ <- lm(pol.score ~ PHQ_MA)
PHQ_pval <- summary(lm_fit_PHQ)$coefficients[2,4]
plot(PHQ_MA, pol.score, main = "PHQ", xlab = c("p-value" ,round(PHQ_pval, digits = 4)), ylab = "Polarity score")
abline(lm_fit_PHQ, col = "red")
```

```{r fig.width=9, fig.height=8.5, echo=FALSE}
BFI_con_MA <- SelfReport_MA[ ,grepl("BFI_Conscious", names(SelfReport_MA))]
BFI_open_MA <- SelfReport_MA[ ,grepl("BFI_Openness", names(SelfReport_MA))]
BFI_agree_MA <- SelfReport_MA[ ,grepl("BFI_Agreeb", names(SelfReport_MA))]
BFI_extrav_MA <- SelfReport_MA[ ,grepl("BFI_Extrav", names(SelfReport_MA))]
BFI_neurot_MA <- SelfReport_MA[ ,grepl("BFI_Neurot", names(SelfReport_MA))]

# Positive score as dependent measure
par(mfrow = c(4, 5))
lm_fit_BFI.con <- lm(pos.score ~ BFI_con_MA)
BFI.con_pval <- summary(lm_fit_BFI.con)$coefficients[2,4]
plot(BFI_con_MA, pos.score, main = "BFI conscious", xlab = c("p-value" ,round(BFI.con_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_BFI.con, col = "red")

lm_fit_BFI.open <- lm(pos.score ~ BFI_open_MA)
BFI.open_pval <- summary(lm_fit_BFI.open)$coefficients[2,4]
plot(BFI_open_MA, pos.score, main = "BFI openness", xlab = c("p-value" ,round(BFI.open_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_BFI.open, col = "red")

lm_fit_BFI.agree <- lm(pos.score ~ BFI_agree_MA)
BFI.agree_pval <- summary(lm_fit_BFI.agree)$coefficients[2,4]
plot(BFI_agree_MA, pos.score, main = "BFI Agreeb", xlab = c("p-value" ,round(BFI.agree_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_BFI.agree, col = "red")

lm_fit_BFI.extrav <- lm(pos.score ~ BFI_extrav_MA)
BFI.extrav_pval <- summary(lm_fit_BFI.extrav)$coefficients[2,4]
plot(BFI_extrav_MA, pos.score, main = "BFI Extrav", xlab = c("p-value" ,round(BFI.extrav_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_BFI.extrav, col = "red")

lm_fit_BFI.neurot <- lm(pos.score ~ BFI_neurot_MA)
BFI.neurot_pval <- summary(lm_fit_BFI.neurot)$coefficients[2,4]
plot(BFI_neurot_MA, pos.score, main = "BFI Neurot", xlab = c("p-value" ,round(BFI.neurot_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_BFI.neurot, col = "red")

# Negative score as dependent measure
lm_fit_BFI.con <- lm(neg.score ~ BFI_con_MA)
BFI.con_pval <- summary(lm_fit_BFI.con)$coefficients[2,4]
plot(BFI_con_MA, neg.score, main = "BFI conscious", xlab = c("p-value" ,round(BFI.con_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_BFI.con, col = "red")

lm_fit_BFI.open <- lm(neg.score ~ BFI_open_MA)
BFI.open_pval <- summary(lm_fit_BFI.open)$coefficients[2,4]
plot(BFI_open_MA, neg.score, main = "BFI openness", xlab = c("p-value" ,round(BFI.open_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_BFI.open, col = "red")

lm_fit_BFI.agree <- lm(neg.score ~ BFI_agree_MA)
BFI.agree_pval <- summary(lm_fit_BFI.agree)$coefficients[2,4]
plot(BFI_agree_MA, neg.score, main = "BFI Agreeb", xlab = c("p-value" ,round(BFI.agree_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_BFI.agree, col = "red")

lm_fit_BFI.extrav <- lm(neg.score ~ BFI_extrav_MA)
BFI.extrav_pval <- summary(lm_fit_BFI.extrav)$coefficients[2,4]
plot(BFI_extrav_MA, neg.score, main = "BFI Extrav", xlab = c("p-value" ,round(BFI.extrav_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_BFI.extrav, col = "red")

lm_fit_BFI.neurot <- lm(neg.score ~ BFI_neurot_MA)
BFI.neurot_pval <- summary(lm_fit_BFI.neurot)$coefficients[2,4]
plot(BFI_neurot_MA, neg.score, main = "BFI Neurot", xlab = c("p-value" ,round(BFI.neurot_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_BFI.neurot, col = "red")

# objectivity score as dependent measure
lm_fit_BFI.con <- lm(obj.score ~ BFI_con_MA)
BFI.con_pval <- summary(lm_fit_BFI.con)$coefficients[2,4]
plot(BFI_con_MA, obj.score, main = "BFI conscious", xlab = c("p-value" ,round(BFI.con_pval, digits = 4)), ylab = "objectivity score")
abline(lm_fit_BFI.con, col = "red")

lm_fit_BFI.open <- lm(obj.score ~ BFI_open_MA)
BFI.open_pval <- summary(lm_fit_BFI.open)$coefficients[2,4]
plot(BFI_open_MA, obj.score, main = "BFI openness", xlab = c("p-value" ,round(BFI.open_pval, digits = 4)), ylab = "objectivity score")
abline(lm_fit_BFI.open, col = "red")

lm_fit_BFI.agree <- lm(obj.score ~ BFI_agree_MA)
BFI.agree_pval <- summary(lm_fit_BFI.agree)$coefficients[2,4]
plot(BFI_agree_MA, obj.score, main = "BFI Agreeb", xlab = c("p-value" ,round(BFI.agree_pval, digits = 4)), ylab = "objectivity score")
abline(lm_fit_BFI.agree, col = "red")

lm_fit_BFI.extrav <- lm(obj.score ~ BFI_extrav_MA)
BFI.extrav_pval <- summary(lm_fit_BFI.extrav)$coefficients[2,4]
plot(BFI_extrav_MA, obj.score, main = "BFI Extrav", xlab = c("p-value" ,round(BFI.extrav_pval, digits = 4)), ylab = "objectivity score")
abline(lm_fit_BFI.extrav, col = "red")

lm_fit_BFI.neurot <- lm(obj.score ~ BFI_neurot_MA)
BFI.neurot_pval <- summary(lm_fit_BFI.neurot)$coefficients[2,4]
plot(BFI_neurot_MA, obj.score, main = "BFI Neurot", xlab = c("p-value" ,round(BFI.neurot_pval, digits = 4)), ylab = "objectivity score")
abline(lm_fit_BFI.neurot, col = "red")

# Polarity score as dependent measure
lm_fit_BFI.con <- lm(pol.score ~ BFI_con_MA)
BFI.con_pval <- summary(lm_fit_BFI.con)$coefficients[2,4]
plot(BFI_con_MA, pol.score, main = "BFI conscious", xlab = c("p-value" ,round(BFI.con_pval, digits = 4)), ylab = "Polarity score")
abline(lm_fit_BFI.con, col = "red")

lm_fit_BFI.open <- lm(pol.score ~ BFI_open_MA)
BFI.open_pval <- summary(lm_fit_BFI.open)$coefficients[2,4]
plot(BFI_open_MA, pol.score, main = "BFI openness", xlab = c("p-value" ,round(BFI.open_pval, digits = 4)), ylab = "Polarity score")
abline(lm_fit_BFI.open, col = "red")

lm_fit_BFI.agree <- lm(pol.score ~ BFI_agree_MA)
BFI.agree_pval <- summary(lm_fit_BFI.agree)$coefficients[2,4]
plot(BFI_agree_MA, pol.score, main = "BFI Agreeb", xlab = c("p-value" ,round(BFI.agree_pval, digits = 4)), ylab = "Polarity score")
abline(lm_fit_BFI.agree, col = "red")

lm_fit_BFI.extrav <- lm(pol.score ~ BFI_extrav_MA)
BFI.extrav_pval <- summary(lm_fit_BFI.extrav)$coefficients[2,4]
plot(BFI_extrav_MA, pol.score, main = "BFI Extrav", xlab = c("p-value" ,round(BFI.extrav_pval, digits = 4)), ylab = "Polarity score")
abline(lm_fit_BFI.extrav, col = "red")

lm_fit_BFI.neurot <- lm(pol.score ~ BFI_neurot_MA)
BFI.neurot_pval <- summary(lm_fit_BFI.neurot)$coefficients[2,4]
plot(BFI_neurot_MA, pol.score, main = "BFI Neurot", xlab = c("p-value" ,round(BFI.neurot_pval, digits = 4)), ylab = "Polarity score")
abline(lm_fit_BFI.neurot, col = "red")
```

- Determine the relationship with respect to the following trait variables:
(Symptom scales OASIS), PROMIS (anxiety, depression, anger))

```{r fig.width=9, fig.height=8.5, echo=FALSE}
OASIS_MA <- case.control_stat_MA$OASIS
PROMIS.Ang_MA <- SelfReport_MA[ ,grepl("PROMIS_AngerTscore", names(SelfReport_MA))]
PROMIS.Dep_MA <- SelfReport_MA[ , grepl("PROMIS_DepressTscore", names(SelfReport_MA))]
PROMIS.Anx_MA <- SelfReport_MA[ , grepl("PROMIS_AnxietyTscore", names(SelfReport_MA))]

# Positive score as dependent measure
par(mfrow = c(4, 4))
lm_fit_OASIS <- lm(pos.score ~ OASIS_MA)
OASIS_pval <- summary(lm_fit_OASIS)$coefficients[2,4]
plot(OASIS_MA, pos.score, main = "OASIS", xlab =c("p-value" ,round(OASIS_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_OASIS, col = "red")

lm_fit_PROMIS.Ang <- lm(pos.score ~ PROMIS.Ang_MA)
PROMIS.Ang_pval <- summary(lm_fit_PROMIS.Ang)$coefficients[2,4]
plot(PROMIS.Ang_MA, pos.score, main = "PROMIS Anger", xlab = c("p-value" ,round(PROMIS.Ang_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_PROMIS.Ang, col = "red")

lm_fit_PROMIS.Dep <- lm(pos.score ~ PROMIS.Dep_MA)
PROMIS.Dep_pval <- summary(lm_fit_PROMIS.Dep)$coefficients[2,4]
plot(PROMIS.Dep_MA, pos.score, main = "PROMIS Depress", xlab = c("p-value" ,round(PROMIS.Dep_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_PROMIS.Dep, col = "red")

lm_fit_PROMIS.Anx <- lm(pos.score ~ PROMIS.Anx_MA)
PROMIS.Anx_pval <- summary(lm_fit_PROMIS.Anx)$coefficients[2,4]
plot(PROMIS.Anx_MA, pos.score, main = "PROMIS Anxiety", xlab =c("p-value" ,round(PROMIS.Anx_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_PROMIS.Anx, col = "red")

# Negative score as dependent measure
lm_fit_OASIS <- lm(neg.score ~ OASIS_MA)
OASIS_pval <- summary(lm_fit_OASIS)$coefficients[2,4]
plot(OASIS_MA, neg.score, main = "OASIS", xlab = c("p-value" ,round(OASIS_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_OASIS, col = "red")

lm_fit_PROMIS.Ang <- lm(neg.score ~ PROMIS.Ang_MA)
PROMIS.Ang_pval <- summary(lm_fit_PROMIS.Ang)$coefficients[2,4]
plot(PROMIS.Ang_MA, neg.score, main = "PROMIS Anger", xlab = c("p-value" ,round(PROMIS.Ang_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_PROMIS.Ang, col = "red")

lm_fit_PROMIS.Dep <- lm(neg.score ~ PROMIS.Dep_MA)
PROMIS.Dep_pval <- summary(lm_fit_PROMIS.Dep)$coefficients[2,4]
plot(PROMIS.Dep_MA, neg.score, main = "PROMIS Depress", xlab = c("p-value" ,round(PROMIS.Dep_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_PROMIS.Dep, col = "red")

lm_fit_PROMIS.Anx <- lm(neg.score ~ PROMIS.Anx_MA)
PROMIS.Anx_pval <- summary(lm_fit_PROMIS.Anx)$coefficients[2,4]
plot(PROMIS.Anx_MA, neg.score, main = "PROMIS Anxiety", xlab = c("p-value" ,round(PROMIS.Anx_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_PROMIS.Anx, col = "red")

# objectivity score as dependent measure
lm_fit_OASIS <- lm(obj.score ~ OASIS_MA)
OASIS_pval <- summary(lm_fit_OASIS)$coefficients[2,4]
plot(OASIS_MA, obj.score, main = "OASIS", xlab = c("p-value" ,round(OASIS_pval, digits = 4)), ylab = "objectivity score")
abline(lm_fit_OASIS, col = "red")

lm_fit_PROMIS.Ang <- lm(obj.score ~ PROMIS.Ang_MA)
PROMIS.Ang_pval <- summary(lm_fit_PROMIS.Ang)$coefficients[2,4]
plot(PROMIS.Ang_MA, obj.score, main = "PROMIS Anger", xlab =c("p-value" ,round(PROMIS.Ang_pval, digits = 4)), ylab = "objectivity score")
abline(lm_fit_PROMIS.Ang, col = "red")

lm_fit_PROMIS.Dep <- lm(obj.score ~ PROMIS.Dep_MA)
PROMIS.Dep_pval <- summary(lm_fit_PROMIS.Dep)$coefficients[2,4]
plot(PROMIS.Dep_MA, obj.score, main = "PROMIS Depress", xlab = c("p-value" ,round(PROMIS.Dep_pval, digits = 4)), ylab = "objectivity score")
abline(lm_fit_PROMIS.Dep, col = "red")

lm_fit_PROMIS.Anx <- lm(obj.score ~ PROMIS.Anx_MA)
PROMIS.Anx_pval <- summary(lm_fit_PROMIS.Anx)$coefficients[2,4]
plot(PROMIS.Anx_MA, obj.score, main = "PROMIS Anxiety", xlab = c("p-value" ,round(PROMIS.Anx_pval, digits = 4)), ylab = "objectivity score")
abline(lm_fit_PROMIS.Anx, col = "red")

# Polarity score as dependent measure
lm_fit_OASIS <- lm(pol.score ~ OASIS_MA)
OASIS_pval <- summary(lm_fit_OASIS)$coefficients[2,4]
plot(OASIS_MA, pol.score, main = "OASIS", xlab = c("p-value" ,round(OASIS_pval, digits = 4)), ylab = "Polarity score")
abline(lm_fit_OASIS, col = "red")

lm_fit_PROMIS.Ang <- lm(pol.score ~ PROMIS.Ang_MA)
PROMIS.Ang_pval <- summary(lm_fit_PROMIS.Ang)$coefficients[2,4]
plot(PROMIS.Ang_MA, pol.score, main = "PROMIS Anger", xlab =c("p-value" ,round(PROMIS.Ang_pval, digits = 4)), ylab = "Polarity score")
abline(lm_fit_PROMIS.Ang, col = "red")

lm_fit_PROMIS.Dep <- lm(pol.score ~ PROMIS.Dep_MA)
PROMIS.Dep_pval <- summary(lm_fit_PROMIS.Dep)$coefficients[2,4]
plot(PROMIS.Dep_MA, pol.score, main = "PROMIS Depress", xlab = c("p-value" ,round(PROMIS.Dep_pval, digits = 4)), ylab = "Polarity score")
abline(lm_fit_PROMIS.Dep, col = "red")

lm_fit_PROMIS.Anx <- lm(pol.score ~ PROMIS.Anx_MA)
PROMIS.Anx_pval <- summary(lm_fit_PROMIS.Anx)$coefficients[2,4]
plot(PROMIS.Anx_MA, pol.score, main = "PROMIS Anxiety", xlab = c("p-value" ,round(PROMIS.Anx_pval, digits = 4)), ylab = "Polarity score")
abline(lm_fit_PROMIS.Anx, col = "red")
```

- Determine mediating influences (CTQ, TEC)on dependent measured scores

```{r fig.width=8, fig.height=7, echo=FALSE}
CTQ_MA <- SelfReport_MA[ ,grepl("CTQ_score", names(SelfReport_MA))]
TES_MA <- SelfReport_MA[ ,grepl("TES_TotalOccurrence", names(SelfReport_MA))]
DAST_MA <- case.control_stat_MA[ ,grepl("DAST", names(SelfReport_MA))]

# mood and anxiety
# Positive score as dependent measure
par(mfcol = c(3, 4))
lm_fit_CTQ <- lm(pos.score ~ CTQ_MA)
CTQ_pval <- summary(lm_fit_CTQ)$coefficients[2,4]
plot(CTQ_MA, pos.score, main = "CTQ", xlab = c("p-value" ,round(CTQ_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_CTQ, col = "red")

lm_fit_TES <- lm(pos.score ~ TES_MA)
TES_pval <- summary(lm_fit_TES)$coefficients[2,4]
plot(TES_MA, pos.score, main = "TES", xlab = c("p-value" ,round(TES_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_TES, col = "red")

lm_fit_DAST <- lm(pos.score ~ DAST_MA)
DAST_pval <- summary(lm_fit_DAST)$coefficients[2,4]
plot(DAST_MA, pos.score, main = "DAST", xlab = c("p-value" ,round(DAST_pval, digits = 4)), ylab = "Positive score")
abline(lm_fit_DAST, col = "red")

# Negative score as dependent measure
lm_fit_CTQ <- lm(neg.score ~ CTQ_MA)
CTQ_pval <- summary(lm_fit_CTQ)$coefficients[2,4]
plot(CTQ_MA, neg.score, main = "CTQ", xlab =c("p-value" ,round(CTQ_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_CTQ, col = "red")

lm_fit_TES <- lm(neg.score ~ TES_MA)
TES_pval <- summary(lm_fit_TES)$coefficients[2,4]
plot(TES_MA, neg.score, main = "TES", xlab = c("p-value" ,round(TES_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_TES, col = "red")

lm_fit_DAST <- lm(neg.score ~ DAST_MA)
DAST_pval <- summary(lm_fit_DAST)$coefficients[2,4]
plot(DAST_MA, neg.score, main = "DAST", xlab = c("p-value" ,round(DAST_pval, digits = 4)), ylab = "Negative score")
abline(lm_fit_DAST, col = "red")

# objectivity score as dependent measure
lm_fit_CTQ <- lm(obj.score ~ CTQ_MA)
CTQ_pval <- summary(lm_fit_CTQ)$coefficients[2,4]
plot(CTQ_MA, obj.score, main = "CTQ", xlab = c("p-value" ,round(CTQ_pval, digits = 4)), ylab = "objectivity score")
abline(lm_fit_CTQ, col = "red")

lm_fit_TES <- lm(obj.score ~ TES_MA)
TES_pval <- summary(lm_fit_TES)$coefficients[2,4]
plot(TES_MA, obj.score, main = "TES", xlab = c("p-value" ,round(TES_pval, digits = 4)), ylab = "objectivity score")
abline(lm_fit_TES, col = "red")

lm_fit_DAST <- lm(obj.score ~ DAST_MA)
DAST_pval <- summary(lm_fit_DAST)$coefficients[2,4]
plot(DAST_MA, obj.score, main = "DAST", xlab = c("p-value" ,round(DAST_pval, digits = 4)), ylab = "objectivity score")
abline(lm_fit_DAST, col = "red")

# Polarity score as dependent measure
lm_fit_CTQ <- lm(pol.score ~ CTQ_MA)
CTQ_pval <- summary(lm_fit_CTQ)$coefficients[2,4]
plot(CTQ_MA, pol.score, main = "CTQ", xlab = c("p-value" ,round(CTQ_pval, digits = 4)), ylab = "Polarity score")
abline(lm_fit_CTQ, col = "red")

lm_fit_TES <- lm(pol.score ~ TES_MA)
TES_pval <- summary(lm_fit_TES)$coefficients[2,4]
plot(TES_MA, pol.score, main = "TES", xlab = c("p-value" ,round(TES_pval, digits = 4)), ylab = "Polarity score")
abline(lm_fit_TES, col = "red")

lm_fit_DAST <- lm(pol.score ~ DAST_MA)
DAST_pval <- summary(lm_fit_DAST)$coefficients[2,4]
plot(DAST_MA, pol.score, main = "DAST", xlab = c("p-value" ,round(DAST_pval, digits = 4)), ylab = "Polarity score")
abline(lm_fit_DAST, col = "red")
```

